---
name: Yue
surname: Hu
position: "Assistant Professor"
address: "Department of Political Science, Tsinghua University, China"
www: sammo3182.github.io
email: yuehu@tsinghua.edu.cn
github: sammo3182
twitter: yuehupolisci
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "414141"
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=multiple-bibliographies.lua"] # used for creating bibliographies for multiple section
header-includes:
- \usepackage{ctex}
csl: apa.csl # to show the entire list of the authors
bibliography_published: "My_Publications.bib" # use separate .bib files and assign each of them a unique key: bibliography_*
bibliography_chinese: "My_Chinese.bib"
bibliography_software: "My_Software.bib"
bibliography_conference: "My_Conference.bib"
nocite: '@*' # don't change this if you want to print out all the refs
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE)

# R packages --------------------------------------------------------------
if (!require(pacman)) install.packages("pacman"); library(pacman)

p_load_gh("ropenscilabs/tic", "mitchelloharawild/vitae")
p_load(tinytex, scholar, tidyverse, here, readxl, glue, bibtex, rorcid, lubridate, vitae)


# Get latex ---------------------------------------------------------------

## This needs to be run manually if LaTex is not installed locally.
##tinytex::install_tinytex()

```

```{r orcidData, include=FALSE}

orcidID <- "0000-0002-2829-3971"

## Education
df_edu <- rorcid::orcid_educations(orcidID)[[orcidID]]$`affiliation-group`$summaries%>%
  data.table::rbindlist(fill=T)

### edu_info<-c("education-summary.department-name","education-summary.role-title","education-summary.start-date.year.value","education-summary.end-date.year.value","education-summary.organization.name","education-summary.organization.address.country")

## Qualifications

df_qualifications <- rorcid::orcid_qualifications(orcidID)[[orcidID]]$`affiliation-group`$summaries%>%
  data.table::rbindlist(fill=T)

### qualifications_info<-c("qualification-summary.organization.name","qualification-summary.role-title","qualification-summary.end-date.year.value","qualification-summary.end-date.month.value","qualification-summary.organization.address.country")

## jobs
ProfessionalPositions <-
  orcid_employments(orcidID)[[orcidID]]$`affiliation-group`$summaries

for (i in 1:length(ProfessionalPositions)) {
  if(length(ProfessionalPositions[[i]])==27)
      {ProfessionalPositions[[i]]$`employment-summary.end-date.year.value` <- "Present"
      ProfessionalPositions[[i]]$`employment-summary.end-date.month.value` <- ""}
}

df_position<-data.table::rbindlist(ProfessionalPositions,fill = T)

# ## works
# benchmark_orcid <- function(id) {
#   tictoc::tic()
# 
#   # Get put-codes
#   put_codes = orcid_works(id)[[1]] %>%  
#     bind_rows() %>% 
#     pull(`put-code`)
# 
#   # Get info of those put codes
#   list_orcid <- orcid_works(id, put_code = put_codes) #%>% bind_rows()
#   cat(id, " - ")
# 
#   tictoc::toc()
#   list_orcid
# }
# 
# works_raw<-benchmark_orcid(orcidID)[[orcidID]][["works"]]
# df_works <-within(works_raw,{
#   authors<-NA
#   authors <- str_extract(`work.citation.citation-value`,"(?<=author=\\s\\{).*(?=\\}, year)")%>%
#     str_replace_all(c("\\{"="","\\}"=""))
# })

##membership
df_membership <- orcid_memberships(orcidID)[[orcidID]][["affiliation-group"]][["summaries"]]%>%
  data.table::rbindlist(fill=T)
# membership_info <- c("membership-summary.organization.name","membership-summary.organization.address.country")

#Grants

df_grants <- orcid_distinctions(orcidID)[[orcidID]][["affiliation-group"]][["summaries"]]%>%
  data.table::rbindlist(fill = T)

```

# Education 

```{r Education}
df_edu %>%
  detailed_entries(
    with = glue::glue("{`education-summary.role-title`} ({`education-summary.department-name`}) "),
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    what = `education-summary.organization.name`,
    where = `education-summary.organization.address.country`
  )
```

## Professional Training

```{r Qualifications}
df_qualifications%>%
  detailed_entries(
    with = `qualification-summary.role-title`,
    when = glue::glue("{`qualification-summary.end-date.year.value`} - {`qualification-summary.end-date.month.value`}"),
    what = `qualification-summary.organization.name`,
    where = `qualification-summary.organization.address.country`
  )
```

# Professional Positions
```{r ProfessionalPositions}
df_position %>% 
  detailed_entries(
    what = `employment-summary.organization.name`,
    when = glue("{`employment-summary.start-date.year.value`}.{`employment-summary.start-date.month.value`}--{`employment-summary.end-date.year.value`}.{`employment-summary.end-date.month.value`}"),
    with = `employment-summary.role-title`,
    where = `employment-summary.organization.address.country`,)
```

# Publications

## Peer-Reviewed Articles

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_published}
:::

\endgroup

## Chinese Articles

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_chinese}
:::

\endgroup

## Software

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_software}
:::

\endgroup

# Conferences

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_conference}
:::

\endgroup


# Grants
```{r grants}
df_grants%>%
  detailed_entries(
    with = `distinction-summary.role-title`,
    what = `distinction-summary.organization.name`,
    when = `distinction-summary.start-date.year.value`,
    )
```

# Skills

## Analytical

R, STATA, Python, C++, Mathematica, NetLogo, JAGS, UCINET.

## Application

LaTeX, Markdown, Git

## Language

Language: English, Chinese (Mandarin)


# Professional Affiliation

Member of 

* American Political Science Association
* Midwest Political Science Association
* Association of Chinese Political Studies

# Teaching

```{r teaching}
tribble(
  ~Year, ~Name, ~Institution,
  'Fall', "70700173: Analysis of Political Data","Tsinghua University",
  'Fall', "80700673: Governmental Big Data","Tsinghua University",
  'Spring', "30700953: Analysis of Public Policy: Perspectives and Methods","Tsinghua University",
  'Summer', "Workshop: Data Visualization","Tsinghua University",
  'Summer', "Workshop: Learning R with Dr. Hu","Tsinghua University",
  'Fall 2018', "POLI301: Analysis of Political Data","University of Iowa",
) %>% 
  detailed_entries(
    when = Year,
    with = Name, 
    where = Institution
  )
```
