---
output: 
  rticles::ctex:
  ## pdf_document:
    keep_tex: yes
    template: svm-latex-cv.tex
geometry: margin=1in

chinese: TRUE

title: "CV"
author: Yue Hu

address: "Mingzhai 114, Qinghua Yuan, Haidian District, Beijing 100084, China"
fontawesome: yes
email: yuehu@tsinghua.edu.cn
github: sammo3182
web: sammo3182.github.io
updated: false
fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 10.5pt
linkcolor: blue
urlcolor: blue
---

```{r setup, include=FALSE}
library(RefManageR)
ajps_mimic <- RefManageR:::MakeBibLaTeX()
with(ajps_mimic,{
  ajps_mimic$fmtJournal <- function(s){
                                if (length(s$journaltitle)) {
                                    res <- emph(cleanupLatex(s$journaltitle))
                                    if (length(s$journalsubtitle))
                                        res <- paste(addPeriod(res), emph(cleanupLatex(s$journalsubtitle)))
                                    return(res)
                                }
                                else if (!is.null(s$journal)) {
                                    emph(cleanupLatex(s$journal))
                                }
     }
     
     ajps_mimic$fmtURL <- function (paper) {
        if (length(paper[["url"]])) {
            res <- paper$url
            res <- switch(docstyle, html = paste0("\\url{", 
                res, "}"), markdown = paste0("[", res, "](", 
                res, ")"), paste0("\\url{", res, "}"))
            if (length(paper$urldate)) {
                fDate <- try(ProcessDate(paper$urldate, NULL), TRUE)
                if (!is.null(fDate) && !inherits(fDate, "try-error")) 
                    res <- paste0(res, " (visited on ", DateFormatter(fDate, 
                      TRUE), ")")
            }
            addPeriod(res)
        }
        else if (length(paper$urldate)) {
            fDate <- try(ProcessDate(paper$urldate, NULL), TRUE)
            if (!is.null(fDate) && !inherits(fDate, "try-error")) 
                paste0("(Visited on ", DateFormatter(fDate, TRUE), 
                    ").")
        }
     }
     
     ajps_mimic$fmtLanguage <- function(lang) {
    if (length(lang) && tolower(lang) != "english") 
        paste0("[", sub("\\b(\\w)", "\\U\\1", lang, perl = TRUE, 
            useBytes = TRUE),"]")
       }
     
     ajps_mimic$formatArticle <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtJTitle(paper$title), fmtLanguage(paper$language), 
        fmtAddOn(paper$titleaddon),
        fmtTranslator(paper), fmtCommentator(paper$commentator), 
        fmtAnnotator(paper$annotator), fmtVersion(paper$version), 
        sentenceP(paste0(c(paste0(c(fmtJournal(paper), fmtSeries(paper$series)), 
            collapse = ""), fmtVolume(paper$volume, paper$number), 
            fmtJournDate(paper)), collapse = " "), fmtBTitle(paper$issuetitle, 
            paper$issuesubtitle), fmtEditor(paper, suffix = NULL, 
            prefix = ". "), fmtNote(paper$note, prefix = ". ", 
            suffix = NULL), pgs = fmtPages(paper$pages, paper$pagination), 
            sep = ""),fmtURL(paper), fmtAddendum(paper$addendum), 
        fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatArticle <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtJTitle(paper$title), fmtLanguage(paper$language), 
        fmtAddOn(paper$titleaddon),
        fmtTranslator(paper), fmtCommentator(paper$commentator), 
        fmtAnnotator(paper$annotator), fmtVersion(paper$version), 
        sentenceP(paste0(c(paste0(c(fmtJournal(paper), fmtSeries(paper$series)), 
            collapse = ""), fmtVolume(paper$volume, paper$number), 
            fmtJournDate(paper)), collapse = " "), fmtBTitle(paper$issuetitle, 
            paper$issuesubtitle), fmtEditor(paper, suffix = NULL, 
            prefix = ". "), fmtNote(paper$note, prefix = ". ", 
            suffix = NULL), pgs = fmtPages(paper$pages, paper$pagination), 
            sep = ""),fmtURL(paper), fmtAddendum(paper$addendum), 
        fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatUnpublished <- function (paper) {
        collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtIBTitle(paper$title, 
            paper$subtitle, FALSE), fmtAddOn(paper$titleaddon), fmtLanguage(paper$language), 
            fmtHowPublished(paper$howpublished), fmtNote(paper$note), 
            sentence(fmtPublisher(NULL, paper$location, paper$address), sep = ""), fmtDOI(paper$doi), 
            fmtURL(paper), fmtAddendum(paper$addendum), fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatMisc <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtIBTitle(paper$title, 
            paper$subtitle, FALSE), fmtAddOn(paper$titleaddon), fmtLanguage(paper$language), 
        fmtEditor(paper, !length(paper$author)), fmtHowPublished(paper$howpublished), 
        addPeriod(fmtType(paper$type)), fmtVersion(paper$version), 
        fmtNote(paper$note), sentence(fmtPublisher(paper$organization, 
            paper$location, paper$address), fmtDate(attr(paper, 
            "dateobj")), sep = ""), fmtDOI(paper$doi), fmtEprint(paper), 
        fmtURL(paper), fmtAddendum(paper$addendum), fmtPubstate(paper$pubstate)))
}
})


tools::bibstyle("ajps_mimic", ajps_mimic)

bib <- ReadBib("publication.bib", check = FALSE)
BibOptions(check.entries = FALSE, 
           first.inits = FALSE,
           bib.style = "ajps_mimic",
           style = "latex",
           max.names = 4,
           dashed = FALSE,
           sorting = "ydnt")
```


# Education
## Degree
* Ph.D. in Political Science, The University of Iowa, U.S.A.\hfill 2018-05
* M.A. in Political Science, The University of South Carolina, U.S.A.\hfill 2013-12
* M.A. in Political Science, The University of Regina, Canada\hfill 2011-03
* LL.B. in International Politics, Nankai University, China\hfill 2009-06

## Additional Training
* Certificate in Informatics, The University of Iowa, U.S.A.\hfill 2016-12
* Experimental Methods, National University of Singapore (IPSA), Singapore \hfill 2014-06/07

# Professional Positions
* Assistant Professor, Department of Political Science, Tsinghua University. \hfill 2019-01/present
* Statistical Consultant, Iowa Social Science Research Center, University of Iowa. \hfill 2015-08/2018-05

# Research Interests
* *Comparative Politics*: Language politics, inequality, political communication.
* *Political Methodology*: Political experiment, text analysis, spatial analysis, network analysis.
* *International Relations*: Soft power, public diplomacy, Chinese foreign policy.

# Publications
## Peer-Reviewed Journal Articles
```{r echo = FALSE, results = "asis", warning=FALSE}
bib[group = "published"]
```

## Journal Articles in Chinese
Yue Hu and Yuchao Zhu. “‘Issue-Oriented’ vs. ‘Ism-Oriented’: Indigenizing Political Science in China?”. *Tianjin Social Science* 3 (2011), pp. 46-50. (胡悦和朱毓朝：《"问题与主义"导向之争: 西方比较政治学沿革及其借鉴意义》，载《天津社会科学》，2011年第3期，第46-50页。)

Tongshun Cheng and Yue Hu. “The Cultural Props of Foreign Policy”. *Tribune of Study* (2010), pp. 33--37.
(程同顺和胡悦：《对外政策的文化道具：浅析文明冲突论的工具性》，载《学习论坛》2010年第26期，第33-37页。)

Yue Hu. “An Analysis of Politics Fixed Position of CPPCC from the Political Scientific Angle”. *Journal of Tianjin Institute of Socialism* (2009), pp. 19--23.
(《从政治科学角度分析人民政协的政治定位》，载《天津市社会主义学院学报》 2009年第1期，第19-23页。)

## Software
```{r echo = FALSE, results = "asis"}
bib[group = "software"]
```

## Under Review

```{r echo = FALSE, results = "asis"}
bib[group = "underreview"]
```

## Working Projects

"Measure Political Desirability: An Experimental Method" (with Wenfang Tang).

"The Logic of Peaceful Rise: Revisiting the Power-Peace Relationship in International Politics" (with Ray Ou-Yang)

"The Popularity of Political Propaganda in Modern China: A Model of Demands" (with Zijie Shao).


# Invited Talks

* 2018
    + "Culture Marker vs. Authority Marker: How Does Language Attitude Affect Political Trust?" Sun Yat-Sen University, Guangzhou, Jan., 3.
* 2017
    + "Investigating Inequality with Real-Life Data: Research Strategies and Methods." Nankai University, Tianjin, Jun., 25.

# Conferences

* 2018
    + "Measuring the Influence of Language in Political Science Research."
        + \footnotesize St. Louis Area Methods Meeting (SLAMM), Ames, Iowa, Apr. 20.
    + "Rebuilding the Tower of Babel? The Influence of Language Policy on Political Trust."
        + \footnotesize Midwest Political Science Association (MPSA) Annual Convention,  Chicago, Illinois, Apr. 5--8.

* 2017
    + "Cultural Accent vs. Authority Accent: How Does Language Attitude Affect Political Trust."
        + \footnotesize Association of Chinese Political Science (ACPS) Annual Meeting, Tianjin, China, Jun., 9--11.
        + \footnotesize Chinese Political Science and Methods Workshop, Shanghai, China, Jul., 8--9.
        + \footnotesize Political Culture, Psychology, and Behavior Research Workshop, Nanjing, China, Jul., 9--11.
    + "The Weight of History: Explaining the Anti-Japanese Sentiments in the Chinese Circle" (with Amy Liu).
        + \footnotesize Midwest Political Science Association (MPSA) Annual Convention,  Chicago, Illinois, Apr. 7--9.
    + "The Popularity of Political Propaganda in Modern China: A Model of Demands" (with Zijie Shao).
        + \footnotesize Midwest Political Science Association (MPSA) Annual Convention,  Chicago, Illinois, Apr. 7--9.
    + "The Logic of Peaceful Rise" (with Ray Ou-Yang).
        + \footnotesize Midwest Political Science Association (MPSA) Annual Convention,  Chicago, Illinois, Apr. 7--9.
        + \footnotesize International Studies Association (ISA) Annual Convention,  Baltimore, Maryland, Feb. 22--25.
        
* 2016
    + "Measure Political Desirability: A List Experimental Method" (with Wenfang Tang);
    + "Propaganda with Museums: A Spatial Analysis of Patriotic Educational Demonstration Bases in China".
        + \footnotesize Association of Chinese Political Science (ACPS) Annual Meeting, Monterey, California, Oct, 10--11.
    + "Value Promotion, Justification, or Mobilization? The Dynamic of the Discourse on Democracy in Modern China."
        + \footnotesize Midwest Political Science Association (MPSA) Annual Conference, Chicago, Apr., 7-10.
* 2015
    + "Affirmative Inaction: Education, Social Mobility, and Ethnic Inequality in China" (with Wenfang Tang and Shuai Jin).
    + "Language and Political Trust."
        + \footnotesize Midwest Political Science Association (MPSA) Annual Conference, Chicago, Apr., 16--19.
* 2013
    + "Connecting Nationalism and Political Transition:A Study of Nationalist Influence on Political Transition based on the China Case."
        + \footnotesize University of South Carolina Inaugural Graduate Student Conference, Columbia, South Carolina.
* 2012
    + "Twofold-Affecting Model: A Cultural Pattern of Social Change from a Comparative Study between the China and Russia Cases."
        + \footnotesize American Association for Chinese Studies (AACS) Annual Conference, Atlanta, Georgia, Oct. 12-14.

# Researching Program
* Youth Project of National Social Science Foundation of China: Assessing and Improving the Political Ecology of Grassroots Party Organizations (ID: 17CZZ041). 
    + Principal Investigator and Methodology Director\hfill 2017/06-2020/06

# Teaching Experience

## University of Tsinghua

* Introduction to Quantitative Political Analysis
* Public Policy
* Inequality: Theories and Measurements

## University of Iowa

* Designing Political Research
* Math Camp for Incoming Graduate Students 
* "Hello, R!" Workshop Series


# Grants
* Ballard and Seashore Fellowship\hfill 2017
* Post-Comprehensive Research Award\hfill 2016
* T. Anne Cleary International Dissertation Research Fellowship\hfill 2016


# Professional Affiliation
* Member of American Political Science Association (& Political Communication Section).
* Member of Midwest Political Science Association.
* Member of Association of Chinese Political Science
* Member of American Association for Chinese Studies.

# Skills
* Analysis & Programming: R, Stata, Python, C++, Mathematica, NetLogo, JAGS, UCINET.
* Application:  \LaTeX, Markdown, Git(GitHub).
* Language: English, Chinese (Mandarin)
