---
output: 
  rticles::ctex:
    keep_tex: yes
    template: svm-latex-cv.tex
geometry: margin=1in

chinese: TRUE

title: "CV"
author: Yue Hu

address: "Mingzhai 114, Qinghua Yuan, Haidian District, Beijing 100084, China"
fontawesome: yes
email: yuehu@tsinghua.edu.cn
github: sammo3182
web: sammo3182.github.io
updated: false
fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 10.5pt
linkcolor: blue
urlcolor: blue
---

```{r setup, include=FALSE}
library(RefManageR)

bib <- ReadBib("My_Publications.bib", check = FALSE)
BibOptions(check.entries = FALSE, 
           first.inits = FALSE,
           bib.style = "authoryear",
           style = "latex",
           max.names = 4,
           dashed = FALSE,
           sorting = "ydnt")
```


# Education
## Degree
* Ph.D. in Political Science, The University of Iowa, U.S.A.\hfill 2018-05
* M.A. in Political Science, The University of South Carolina, U.S.A.\hfill 2013-12
* M.A. in Political Science, The University of Regina, Canada\hfill 2011-06
* LL.B. in International Politics, Nankai University, China\hfill 2009-06

## Additional Training
* Certificate in Informatics, The University of Iowa, U.S.A.\hfill 2016-12
* Experimental Methods, National University of Singapore (IPSA), Singapore \hfill 2014-06/07

# Professional Positions
* Assistant Professor, Department of Political Science, Tsinghua University. \hfill 2019-01/present
* Statistical Consultant, Iowa Social Science Research Center, University of Iowa. \hfill 2015-08/2018-05

# Research Interests
* *Comparative Politics*: Language politics, inequality, political communication.
* *Political Methodology*: Political experiment, text analysis, spatial analysis, network analysis.


# Publications
## Peer-Reviewed Journal Articles
```{r echo = FALSE, results = "asis", warning=FALSE}
bib[bibtype = "article", 
    language = "en"]
```

\vspace{\baselineskip}

## Journal Articles in Chinese
Yue Hu and Yuchao Zhu. “‘Issue-Oriented’ vs. ‘Ism-Oriented’: Indigenizing Political Science in China?”. *Tianjin Social Science* 3 (2011), pp. 46-50. (胡悦和朱毓朝：《"问题与主义"导向之争: 西方比较政治学沿革及其借鉴意义》，载《天津社会科学》，2011年第3期，第46-50页。)

Tongshun Cheng and Yue Hu. “The Cultural Props of Foreign Policy”. *Tribune of Study* (2010), pp. 33--37.
(程同顺和胡悦：《对外政策的文化道具：浅析文明冲突论的工具性》，载《学习论坛》2010年第26期，第33-37页。)

Yue Hu. “An Analysis of Politics Fixed Position of CPPCC from the Political Scientific Angle”. *Journal of Tianjin Institute of Socialism* (2009), pp. 19--23.
(《从政治科学角度分析人民政协的政治定位》，载《天津市社会主义学院学报》 2009年第1期，第19-23页。)

\vspace{\baselineskip}

## Software
```{r echo = FALSE, results = "asis"}
bib[bibtype = "misc"]
```

\vspace{\baselineskip}


# Invited Talks

* 2018
    + "Culture Marker vs. Authority Marker: How Does Language Attitude Affect Political Trust?" Sun Yat-Sen University, Guangzhou, Jan., 3.
* 2017
    + "Investigating Inequality with Real-Life Data: Research Strategies and Methods." Nankai University, Tianjin, Jun., 25.

# Conferences

* 2019
    + "Breaking Through the Linguistic Barrier: The Role of Language Policy in Migration Decisions."
        + \footnotesize American Political Science Association (APSA) Annual Meeting, Washington D.C., Aug. 29--Sep. 01.
    + "Visualization and Going Against P-Hacking."
        + \footnotesize China R Conference, Beijing, May 25--26.
* 2018
    + "Measuring the Influence of Language in Political Science Research."
        + \footnotesize St. Louis Area Methods Meeting (SLAMM), Ames, Iowa, Apr. 20.
    + "Rebuilding the Tower of Babel? The Influence of Language Policy on Political Trust."
        + \footnotesize Midwest Political Science Association (MPSA) Annual Convention, Chicago, Illinois, Apr. 5--8.

* 2017
    + "Cultural Accent vs. Authority Accent: How Does Language Attitude Affect Political Trust."
        + \footnotesize Association of Chinese Political Science (ACPS) Annual Meeting, Tianjin, China, Jun., 9--11.
        + \footnotesize Chinese Political Science and Methods Workshop, Shanghai, China, Jul., 8--9.
        + \footnotesize Political Culture, Psychology, and Behavior Research Workshop, Nanjing, China, Jul., 9--11.
    + "The Weight of History: Explaining the Anti-Japanese Sentiments in the Chinese Circle" (with Amy Liu).
        + \footnotesize Midwest Political Science Association (MPSA) Annual Convention,  Chicago, Illinois, Apr. 7--9.
    + "The Popularity of Political Propaganda in Modern China: A Model of Demands" (with Zijie Shao).
        + \footnotesize Midwest Political Science Association (MPSA) Annual Convention,  Chicago, Illinois, Apr. 7--9.
    + "The Logic of Peaceful Rise" (with Ray Ou-Yang).
        + \footnotesize Midwest Political Science Association (MPSA) Annual Convention,  Chicago, Illinois, Apr. 7--9.
        + \footnotesize International Studies Association (ISA) Annual Convention,  Baltimore, Maryland, Feb. 22--25.
        
* 2016
    + "Measure Political Desirability: A List Experimental Method" (with Wenfang Tang);
    + "Propaganda with Museums: A Spatial Analysis of Patriotic Educational Demonstration Bases in China".
        + \footnotesize Association of Chinese Political Science (ACPS) Annual Meeting, Monterey, California, Oct, 10--11.
    + "Value Promotion, Justification, or Mobilization? The Dynamic of the Discourse on Democracy in Modern China."
        + \footnotesize Midwest Political Science Association (MPSA) Annual Conference, Chicago, Apr., 7-10.
* 2015
    + "Affirmative Inaction: Education, Social Mobility, and Ethnic Inequality in China" (with Wenfang Tang and Shuai Jin).
    + "Language and Political Trust."
        + \footnotesize Midwest Political Science Association (MPSA) Annual Conference, Chicago, Apr., 16--19.
* 2013
    + "Connecting Nationalism and Political Transition:A Study of Nationalist Influence on Political Transition based on the China Case."
        + \footnotesize University of South Carolina Inaugural Graduate Student Conference, Columbia, South Carolina.
* 2012
    + "Twofold-Affecting Model: A Cultural Pattern of Social Change from a Comparative Study between the China and Russia Cases."
        + \footnotesize American Association for Chinese Studies (AACS) Annual Conference, Atlanta, Georgia, Oct. 12-14.

# Researching Program
* Youth Project of National Social Science Foundation of China: Assessing and Improving the Political Ecology of Grassroots Party Organizations (ID: 17CZZ041). 
    + Principal Investigator and Methodology Director\hfill 2017/06-2020/06

# Teaching Experience

## University of Tsinghua

* Analysis of Political Data
* Analysis of Public Policy: Perspectives and Methods
* Governmental Big Data

## University of Iowa

* Designing Political Research
* Math Camp for Incoming Graduate Students 
* "Hello, R!" Workshop Series


# Grants
* Ballard and Seashore Fellowship\hfill 2017
* Post-Comprehensive Research Award\hfill 2016
* T. Anne Cleary International Dissertation Research Fellowship\hfill 2016


# Professional Affiliation
* Member of American Political Science Association.
* Member of Midwest Political Science Association.
* Member of Association of Chinese Political Science
* Member of American Association for Chinese Studies.

# Skills
* Analysis & Programming: R, Stata, Python, C++, Mathematica, NetLogo, JAGS, UCINET.
* Application:  \LaTeX, Markdown, Git(GitHub).
* Language: English, Chinese (Mandarin)
