\documentclass[10.5pt,]{article}

\usepackage{multicol} % for multiple columns



\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{xltxtra,xunicode} %originally, \usepackage{mathspec}. This change is to produce Chinese
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}

	\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
	\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}


% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Yue Hu - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Yue Hu:  CV (Curriculum Vitae)},
            pdfauthor={Yue Hu},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}


\centerline{\huge \bf Yue Hu}

\vspace{2 mm}

\hrule

\vspace{2 mm}


\moveleft.5\hoffset\centerline{313 Schaeffer Hall, 20E Washington Street, Iowa City, IA, 52242}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:yue-hu-1@uiowa.edu}{\nolinkurl{yue-hu-1@uiowa.edu}}} \hspace{1 mm}  \faPhone \hspace{1 mm}  +01-803-250-1686  \hspace{1 mm}  \faGithub \hspace{1 mm} \href{http://github.com/sammo3182}{\tt sammo3182} \hspace{1 mm}    \faGlobe \hspace{1 mm} \href{http://sammo3182.github.io}{\tt sammo3182.github.io}   }

\vspace{2 mm}

\hrule


\section{Education}\label{education}

\subsection{Degree}\label{degree}

\begin{itemize}
\tightlist
\item
  Ph.D.~in Political Science, The University of Iowa,
  U.S.A.\hfill 2018-05 (Expected)

  \begin{itemize}
  \tightlist
  \item
    \footnotesize Dissertation: ``Dominant Language: A Political
    Stabilizer''
  \end{itemize}
\item
  Certificate in Informatics, The University of Iowa,
  U.S.A.\hfill 2016-12
\item
  M.A.~in Political Science, The University of South Carolina,
  U.S.A.\hfill 2013-03

  \begin{itemize}
  \tightlist
  \item
    \footnotesize Thesis: ``Connecting Nationalism and Political
    Transition: A Study of Nationalist Influence on Political Transition
    Based on the Chinese Case.''
  \end{itemize}
\item
  M.A.~in Political Science, The University of Regina,
  Canada\hfill 2011-03

  \begin{itemize}
  \tightlist
  \item
    \footnotesize Thesis: ``Culture and Cultural Diplomacy: A
    Comparative Study of a Canadian and Chinese Case.''
  \end{itemize}
\item
  LL.B. in International Politics, Nankai University,
  China\hfill 2009-06
\end{itemize}

\subsection{Additional Training}\label{additional-training}

\begin{itemize}
\tightlist
\item
  Experimental Methods \hfill 2014-06/07

  \begin{itemize}
  \tightlist
  \item
    \footnotesize IPSA-NUS Summer School of Social Science Research
    Methods, Singapore.
  \end{itemize}
\end{itemize}

\section{Professional Positions}\label{professional-positions}

\begin{itemize}
\tightlist
\item
  Statistical Consultant, Iowa Social Science Research Center,
  University of Iowa.
\end{itemize}

\section{Research Interests}\label{research-interests}

\begin{itemize}
\tightlist
\item
  Comparative Politics:

  \begin{itemize}
  \tightlist
  \item
    Language Policy, Chinese politics, public opinion, political
    communication, political culture.
  \end{itemize}
\item
  Political Methodology:

  \begin{itemize}
  \tightlist
  \item
    Survey experiment, text analysis, network analysis, spatial
    analysis, multilevel analysis.
  \end{itemize}
\item
  International Relations:

  \begin{itemize}
  \tightlist
  \item
    Public diplomacy, international cultural relations, Chinese foreign
    policy.
  \end{itemize}
\end{itemize}

\section{Publication}\label{publication}

\subsection{Journal Articles}\label{journal-articles}

Frederick Solt, Yue Hu, Kevan Hudson, Jungmin Song, et al. ``Economic
Inequality and Class Consciousness''. \emph{Journal of Politics} 3
(2017).

Frederick Solt, Yue Hu, Kevan Hudson, Jungmin Song, et al. ``Economic
Inequality and Belief in Meritocracy in the United States''.
\emph{Research and Politics} 3.4 (2016), pp.~1-7.
\url{http://rap.sagepub.com/content/3/4/2053168016672101}.

Wen Fang Tang, Yue Hu and Shuai Jin. ``Affirmative Inaction: Language
Education and Labor Mobility among China's Muslim Minorities''.
\emph{Chinese Sociological Review} 4.48 (2016), pp.~346-66.

Yue Hu. ``Institutional Difference and Cultural Difference: A
Comparative Study of Canadian and Chinese Cultural Diplomacy''.
\emph{Journal of American-East Asian Relations} 20.2-3 (2013),
pp.~256-68.
\url{http://booksandjournals.brillonline.com/content/journals/10.1163/18765610-02003011}.

Yue Hu and Yuchao Zhu. ```Issue-Oriented' vs. `Ism-Oriented':
Indigenizing Political Science in China?'' {[}Chinese{]}
\emph{Tianjin Social Science} 3 (2011), pp.~46-50.

Tongshun Cheng and Yue Hu. ``The Cultural Props of Foreign Policy''.
{[}Chinese{]} \emph{Tribune of Study} (2010), pp.~33--37.

Yue Hu. ``An Analysis of Politics Fixed Position of CPPCC from the
Political Scientific Angle''. {[}Chinese{]}
\emph{Journal of Tianjin Institute of Socialism} 1 (2009), pp.~19-23.

\subsection{Software}\label{software}

Frederick Solt and Yue Hu. ``pewdata: Reproducible Retrieval of Pew
Research Center Datasets''. Available at The Comprehensive R Archive
Network (CRAN). 2016. \url{http://CRAN.R-project.org/package=pewdata}.

Frederick Solt and Yue Hu. ``dotwhisker: Dot-and-Whisker Plots of
Regression Results''. Available at The Comprehensive R Archive Network
(CRAN). 2015. \url{http://CRAN.R-project.org/package=dotwhisker}.

Frederick Solt and Yue Hu. ``interplot: Plot the Effects of Variables in
Interaction Terms''. Available at The Comprehensive R Archive Network
(CRAN). 2015. \url{http://CRAN.R-project.org/package=interplot}.

\subsection{Under Review}\label{under-review}

Vicki Claypool, William Reisinger, Marina Zaloznaya and Yue Hu. ``The
Pernicious Effect of Petty Corruption on System-Supporting Political
Behavior in Post-Soviet States''.

Yue Hu. ``Are Informal Education Facilities Effective Means for
Political Propaganda? A Spatial Analysis''.

Yue Hu. ``Strategic Communication: Why the Chinese Government Engages in
Discourse about Democracy and Why It Matters''.

\subsection{Working Projoects}\label{working-projoects}

``Measure Political Desirability: An Experimental Method'' (with Wenfang
Tang).

``The Weight of History: Explaining the Anti-Japanese Sentiments in the
Chinese Circle'' (with Amy Liu).

``The Logic of Peaceful Rise: Revisiting the Power-Peace Relationship in
International Politics'' (with Ray Ou-Yang)

``The Popularity of Political Propaganda in Modern China: A Model of
Demands'' (with Zijie Yao).

``Niche Audience: Chinese Government's Secret Weapon in Official Media
Propaganda'' (with Zijie Shao).

\subsection{Magazine and Others}\label{magazine-and-others}

Yue Hu. ``Experiences on Document Preparation for Applications to PhD
Programs of American Universities''. {[}Chinese{]} \emph{New Vision} 17
(2014), pp.~37-38.

Yue Hu. ``Nothing Honored, So\ldots{}'' {[}Chinese{]} \emph{New Vision}
(2010), pp.~25-26.

Yue Hu. ``Three Harmonies of Premier Zhou Enlai''. {[}Chinese{]}
\emph{National Spirit} 17 (2007), p.~45.

Yue Hu. ``Philo-mathematics: A Methodology of Politicians.''
{[}Chinese{]} \emph{Beauty of Mathematics} 1 (2006), pp.~157-160.

Yue Hu. ``The Greatness of Open Sources''. {[}Chinese{]}
\emph{LUPA-STAR Essay Compilation} (2006), pp.~24-25.

\section{Conference}\label{conference}

\begin{itemize}
\tightlist
\item
  2017

  \begin{itemize}
  \tightlist
  \item
    ``The Weight of History: Explaining the Anti-Japanese Sentiments in
    the Chinese Circle'' (with Amy Liu).

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Midwest Political Science Association (MPSA) Annual
      Convention, Chicago, Illinois, Apr. 7--9.
    \end{itemize}
  \item
    ``The Popularity of Political Propaganda in Modern China: A Model of
    Demands'' (with Zijie Yao).

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Midwest Political Science Association (MPSA) Annual
      Convention, Chicago, Illinois, Apr. 7--9.
    \end{itemize}
  \item
    ``The Logic of Peaceful Rise'' (with Ray Ou-Yang).

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Midwest Political Science Association (MPSA) Annual
      Convention, Chicago, Illinois, Apr. 7--9.
    \item
      \footnotesize International Studies Association (ISA) Annual
      Convention, Baltimore, Maryland, Feb. 22--25.
    \end{itemize}
  \end{itemize}
\item
  2016

  \begin{itemize}
  \tightlist
  \item
    ``Measure Political Desirability: A List Experimental Method'' (with
    Wenfang Tang);
  \item
    ``Propaganda with Museums: A Spatial Analysis of Patriotic
    Educational Demonstration Bases in China''.

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Association of Chinese Political Science (ACPS)
      Annual Meeting, Monterey, California, Oct, 10--11.
    \end{itemize}
  \item
    ``Value Promotion, Justification, or Mobilization? The Dynamic of
    the Discourse on Democracy in Modern China.''

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Midwest Political Science Association (MPSA) Annual
      Conference, Chicago, Apr., 7-10.
    \end{itemize}
  \end{itemize}
\item
  2015

  \begin{itemize}
  \tightlist
  \item
    ``Affirmative Inaction: Education, Social Mobility, and Ethnic
    Inequality in China'' (with Wenfang Tang and Shuai Jin).
  \item
    ``Language and Political Trust.''

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Midwest Political Science Association (MPSA) Annual
      Conference, Chicago, Apr., 16--19.
    \end{itemize}
  \end{itemize}
\item
  2013

  \begin{itemize}
  \tightlist
  \item
    ``Connecting Nationalism and Political Transition:A Study of
    Nationalist Influence on Political Transition based on the China
    Case.''

    \begin{itemize}
    \tightlist
    \item
      \footnotesize University of South Carolina Inaugural Graduate
      Student Conference, Columbia, South Carolina.
    \end{itemize}
  \end{itemize}
\item
  2012

  \begin{itemize}
  \tightlist
  \item
    ``Twofold-Affecting Model: A Cultural Pattern of Social Change from
    a Comparative Study between the China and Russia cases.''

    \begin{itemize}
    \tightlist
    \item
      \footnotesize American Association for Chinese Studies (AACS)
      Annual Conference, Atlanta, Georgia, Oct. 12-14.
    \end{itemize}
  \end{itemize}
\end{itemize}

\section{Research Experience}\label{research-experience}

\subsection{Data Collection}\label{data-collection}

\begin{itemize}
\tightlist
\item
  Online survey experiment in China.\hfill 2017-02

  \begin{itemize}
  \tightlist
  \item
    \footnotesize Designed an online survey experiments, finished 994
    surveys.
  \end{itemize}
\item
  Field survey experiment in China.\hfill 2016-12

  \begin{itemize}
  \tightlist
  \item
    \footnotesize Designed and conducted survey experiments in Chengdu
    and Meizhou of China on 421 subjects in total.
  \end{itemize}
\item
  Webscrapping Newspaper Documents.\hfill 2016

  \begin{itemize}
  \tightlist
  \item
    \footnotesize Scrapped the text content of \emph{People's Daily}
    (1946-2003) from a third party website, ending with 1,371,607
    documents.
  \end{itemize}
\end{itemize}

\subsection{Research Assistant}\label{research-assistant}

\begin{itemize}
\tightlist
\item
  Corruption and Politics in Russia, Ukraine, and Georgia Project (Univ.
  of Iowa)\hfill 2015-2016
\item
  Standardized World Income Inequality Database Project (Univ. of
  Iowa)\hfill 2015-05/06
\item
  Survey in Eastern Asia Project (Univ. of South
  Carolina)\hfill 2013-05/08
\end{itemize}

\section{Teaching Interest}\label{teaching-interest}

\begin{itemize}
\tightlist
\item
  Comparative Politics:

  \begin{itemize}
  \tightlist
  \item
    Intro to Comparative Politics, Language Policy, Public Opinion,
    Asian Politics, Chinese Politics, Ethnicity, Nationalism,
    Democratization.
  \end{itemize}
\item
  Political Methodology:

  \begin{itemize}
  \tightlist
  \item
    Research Design, Intro to Quantitative Analysis in Social Science,
    Regression, Maximum Likelihood Estimation, Multilevel Modeling,
    Spatial Analysis, Network Analysis, Experiment, Structural Equation
    Modeling, Survey Design and Analysis, Programming in R, Stata, and
    Python, Data Visualization.
  \end{itemize}
\end{itemize}

\section{Teaching Experience}\label{teaching-experience}

\subsection{Instructor, University of
Iowa}\label{instructor-university-of-iowa}

\begin{itemize}
\tightlist
\item
  Introduction To R Workshop Series\hfill 2015-present
\item
  Multilevel Modeling with Stata and R\hfill 2016-present
\item
  Math Camp for Incoming Graduate Students (with Shuai
  Jin)\hfill 2016-08
\end{itemize}

\subsection{Guest Lecture, University of South
Carolina}\label{guest-lecture-university-of-south-carolina}

\begin{itemize}
\tightlist
\item
  Comparative Politics-Developing Countries\hfill Spring 2012
\item
  National Security of United States\hfill Fall 2011
\end{itemize}

\subsection{Teaching Assistant, University of
Iowa}\label{teaching-assistant-university-of-iowa}

\begin{itemize}
\tightlist
\item
  Introduction to Political Behavior\hfill Spring 2015
\item
  Introduction to International Relations\hfill Fall 2014
\item
  Introduction to Comparative Politics\hfill Spring 2014
\item
  Political Campaigning\hfill Fall 2014
\item
  Political Pschology\hfill Fall 2014
\end{itemize}

\subsection{Teaching Assistant, University of South
Carolina}\label{teaching-assistant-university-of-south-carolina}

\begin{itemize}
\tightlist
\item
  International Relations\hfill Spring 2013
\item
  Comparative Politics\hfill Spring 2013
\item
  Controversial World Politics\hfill Fall 2012
\item
  American National Government\hfill Spring 2012
\item
  Comparative Politics-Developing Countries\hfill Spring 2012
\item
  National Security of United States\hfill Fall 2011
\end{itemize}

\subsection{Teaching Assistant, University of
Regina}\label{teaching-assistant-university-of-regina}

\begin{itemize}
\tightlist
\item
  Introduction to Political Science\hfill Fall 2010
\end{itemize}

\section{Grants}\label{grants}

\subsection{Research Awards}\label{research-awards}

\begin{itemize}
\tightlist
\item
  Post-Comprehensive Research Award (\$9404.50)\hfill 2016
\item
  T. Anne Cleary International Dissertation Research Fellowship (\$5000)
  \hfill 2016
\item
  Center of Asian and Pacific Studies Graduate Dissertation Grant
  (\$1000)\hfill 2016
\item
  Best Conference Paper Award of Department of Political Science
  (\$500)\hfill 2016
\item
  Department Summer Training Grant (\$1900)\hfill 2014
\item
  Graduate Research Award, University of Regina\hfill 2010
\item
  Graduate Studies Scholarship, University of Regina\hfill 2009-2011
\item
  City Administration Scholarship, Tianjin Municipal People's
  Government\hfill 2008
\end{itemize}

\subsection{Travel Grants}\label{travel-grants}

\begin{itemize}
\tightlist
\item
  Graduate School Senate Supplemental Travel Funds Award
  (\$600)\hfill 2016
\item
  Graduate \& Professional Student Government Travel Grant
  (\$500)\hfill 2016
\item
  CAPS Graduate Student Conference Travel Award (\$500)\hfill 2015
\item
  Graduate Student Senate Travel Funds Award (\$200)\hfill 2015
\item
  Department Travel Awards (\$500\textasciitilde{}\$800)\hfill 2015-2017
\end{itemize}

\subsection{Graduate Assistantship}\label{graduate-assistantship}

\begin{itemize}
\tightlist
\item
  Graduate Assistantship, University of Iowa\hfill 2014-2017
\item
  Graduate Assistantship, University of South Carolina\hfill 2011-2013
\end{itemize}

\section{Professional Affiliation}\label{professional-affiliation}

\begin{itemize}
\tightlist
\item
  Member of American Political Science Association.
\item
  Member of Midwest Political Science Association.
\item
  Member of Association of Chinese Political Science
\item
  Member of American Association for Chinese Studies.
\end{itemize}

\section{Skills}\label{skills}

\begin{itemize}
\tightlist
\item
  Analysis \& Programming: R, Stata, Python, C++, Mathematica, NetLogo,
  JAGS.
\item
  Application: \LaTeX, Markdown, Git(GitHub).
\item
  Language: English, Chinese (Mandarin)
\end{itemize}

\section{Reference}\label{reference}

\begin{tabular}{ll}
\parbox{5cm}{\textbf{Wenfang Tang}\\Professor\\University of Iowa\\(319)335-2546\\\href{mailto:wenfang-tang@uiowa.edu}{wenfang-tang@uiowa.edu}}
 &\parbox{5cm}{\textbf{William M. Reisinger}\\Professor\\University of Iowa\\(319)335-2351\\\href{mailto:william-reisinger@uiowa.edu}{william-reisinger@uiowa.edu}}\\
&\\
\parbox{5cm}{\textbf{Frederick Solt}\\Associate Professor\\University of Iowa\\(319) 335-2340\\\href{mailto:frederick-solt@uiowa.edu}{frederick-solt@uiowa.edu}}
 &\parbox{5cm}{\textbf{Caroline J. Tolbert}\\Professor\\University of Iowa\\(319) 335-2471\\\href{caroline-tolbert@uiowa.edu}{caroline-tolbert@uiowa.edu}}\\
\end{tabular}

\end{document}
