---
output: 
  rticles::ctex:
  ## pdf_document:
    keep_tex: yes
    template: svm-latex-cv.tex
geometry: margin=1in

chinese: TRUE

title: "CV"
author: Yue Hu

address: "313 Schaeffer Hall, 20E Washington Street, Iowa City, IA, 52242"
fontawesome: yes
email: yue-hu-1@uiowa.edu
github: sammo3182
phone: "+01-803-250-1686"
web: sammo3182.github.io
updated: no
fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 10.5pt
linkcolor: blue
urlcolor: blue
---

```{r setup, include=FALSE}
library(RefManageR)
ajps_mimic <- RefManageR:::MakeBibLaTeX()
with(ajps_mimic,{
  ajps_mimic$fmtJournal <- function(s){
                                if (length(s$journaltitle)) {
                                    res <- emph(cleanupLatex(s$journaltitle))
                                    if (length(s$journalsubtitle))
                                        res <- paste(addPeriod(res), emph(cleanupLatex(s$journalsubtitle)))
                                    return(res)
                                }
                                else if (!is.null(s$journal)) {
                                    emph(cleanupLatex(s$journal))
                                }
     }
     
     ajps_mimic$fmtURL <- function (paper) {
        if (length(paper[["url"]])) {
            res <- paper$url
            res <- switch(docstyle, html = paste0("\\url{", 
                res, "}"), markdown = paste0("[", res, "](", 
                res, ")"), paste0("\\url{", res, "}"))
            if (length(paper$urldate)) {
                fDate <- try(ProcessDate(paper$urldate, NULL), TRUE)
                if (!is.null(fDate) && !inherits(fDate, "try-error")) 
                    res <- paste0(res, " (visited on ", DateFormatter(fDate, 
                      TRUE), ")")
            }
            addPeriod(res)
        }
        else if (length(paper$urldate)) {
            fDate <- try(ProcessDate(paper$urldate, NULL), TRUE)
            if (!is.null(fDate) && !inherits(fDate, "try-error")) 
                paste0("(Visited on ", DateFormatter(fDate, TRUE), 
                    ").")
        }
     }
     
     ajps_mimic$fmtLanguage <- function(lang) {
    if (length(lang) && tolower(lang) != "english") 
        paste0("[", sub("\\b(\\w)", "\\U\\1", lang, perl = TRUE, 
            useBytes = TRUE),"]")
       }
     
     ajps_mimic$formatArticle <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtJTitle(paper$title), fmtLanguage(paper$language), 
        fmtAddOn(paper$titleaddon),
        fmtTranslator(paper), fmtCommentator(paper$commentator), 
        fmtAnnotator(paper$annotator), fmtVersion(paper$version), 
        sentenceP(paste0(c(paste0(c(fmtJournal(paper), fmtSeries(paper$series)), 
            collapse = ""), fmtVolume(paper$volume, paper$number), 
            fmtJournDate(paper)), collapse = " "), fmtBTitle(paper$issuetitle, 
            paper$issuesubtitle), fmtEditor(paper, suffix = NULL, 
            prefix = ". "), fmtNote(paper$note, prefix = ". ", 
            suffix = NULL), pgs = fmtPages(paper$pages, paper$pagination), 
            sep = ""),fmtURL(paper), fmtAddendum(paper$addendum), 
        fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatArticle <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtJTitle(paper$title), fmtLanguage(paper$language), 
        fmtAddOn(paper$titleaddon),
        fmtTranslator(paper), fmtCommentator(paper$commentator), 
        fmtAnnotator(paper$annotator), fmtVersion(paper$version), 
        sentenceP(paste0(c(paste0(c(fmtJournal(paper), fmtSeries(paper$series)), 
            collapse = ""), fmtVolume(paper$volume, paper$number), 
            fmtJournDate(paper)), collapse = " "), fmtBTitle(paper$issuetitle, 
            paper$issuesubtitle), fmtEditor(paper, suffix = NULL, 
            prefix = ". "), fmtNote(paper$note, prefix = ". ", 
            suffix = NULL), pgs = fmtPages(paper$pages, paper$pagination), 
            sep = ""),fmtURL(paper), fmtAddendum(paper$addendum), 
        fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatUnpublished <- function (paper) {
        collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtIBTitle(paper$title, 
            paper$subtitle, FALSE), fmtAddOn(paper$titleaddon), fmtLanguage(paper$language), 
            fmtHowPublished(paper$howpublished), fmtNote(paper$note), 
            sentence(fmtPublisher(NULL, paper$location, paper$address), sep = ""), fmtDOI(paper$doi), 
            fmtURL(paper), fmtAddendum(paper$addendum), fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatMisc <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtIBTitle(paper$title, 
            paper$subtitle, FALSE), fmtAddOn(paper$titleaddon), fmtLanguage(paper$language), 
        fmtEditor(paper, !length(paper$author)), fmtHowPublished(paper$howpublished), 
        addPeriod(fmtType(paper$type)), fmtVersion(paper$version), 
        fmtNote(paper$note), sentence(fmtPublisher(paper$organization, 
            paper$location, paper$address), fmtDate(attr(paper, 
            "dateobj")), sep = ""), fmtDOI(paper$doi), fmtEprint(paper), 
        fmtURL(paper), fmtAddendum(paper$addendum), fmtPubstate(paper$pubstate)))
}
})


tools::bibstyle("ajps_mimic", ajps_mimic)

bib <- ReadBib("publication.bib", check = FALSE)
BibOptions(check.entries = FALSE, 
           first.inits = FALSE,
           bib.style = "ajps_mimic",
           style = "latex",
           max.names = 4,
           dashed = FALSE,
           sorting = "ydnt")
```


# Education
## Degree
* Ph.D. in Political Science, The University of Iowa, U.S.A.\hfill 2018-05 (Expected)
    + \footnotesize Dissertation: "Rebuilding the Tower of Babel: Language Policy and Political Trust in China."
        + Committee Chair: Wenfang Tang
        + Committee Members: William M. Reisinger, Frederick Solt, Caroline J. Tolbert, and David Cassels Johnson (Education)
        + Abstract: My dissertation explores how authoritarian governments use language policy to impact public political trust. Based on a comprehensive examination through survey analyses, experiments, and large-scale text analyses, my research demonstrates that authoritarian governments, such as in China, can also use it as a political tool to influence citizens’ attitudes and even their political value system. Using a computer-assisted text analysis of over one million articles from the official newspaper of the dominant party of China from 1946-2003, I point out that the Chinese government applied a communication strategy redefining the concept of "democracy" not with regime justification but with national policy accomplishments in the Chinese political language. In the meantime, this concept was most frequently deployed alongside the discourses about liberal values. With this strategy, the Chinese political discourse manipulated the meaning of democracy without contradicting with the Western democratic values, while simultaneously preserving the authoritarian regime. Given the size of the dataset, the findings are robust and generalizable. Moreover, by analyzing results of an original experiment in China based on an adjusted sociolinguistic technique, I demonstrated that the single official language policy applied by the Chinese government changes citizens' language attitudes and further their process-based political trust. Drawing on a nationally representative large sample survey from China, my dissertation also identifies direct and indirect paths throughout which the official language affects citizens' institutional-based political trust.
* M.A. in Political Science, The University of South Carolina, U.S.A.\hfill 2013-03
* M.A. in Political Science, The University of Regina, Canada\hfill 2011-03
* LL.B. in International Politics, Nankai University, China\hfill 2009-06

## Additional Training
* Certificate in Informatics, The University of Iowa, U.S.A.\hfill 2016-12
* Experimental Methods, National University of Singapore (IPSA), Singapore \hfill 2014-06/07

# Professional Positions
* Statistical Consultant, Iowa Social Science Research Center, University of Iowa. 2015-08/present

# Research Interests
* *Comparative Politics*: Political communication, language policy, public opinion.
* *Political Methodology*: Survey experiment, text analysis, network analysis, spatial analysis.
* *International Relations*: Public diplomacy, international cultural relations, Chinese foreign policy.

# Publications
## Peer-Reviewed Journal Articles
```{r echo = FALSE, results = "asis", warning=FALSE}
bib[group = "published"][c(1,2,6,7)]
```

## Journal Articles in Chinese
Yue Hu and Yuchao Zhu. “‘Issue-Oriented’ vs. ‘Ism-Oriented’: Indigenizing Political Science in China?”. *Tianjin Social Science* 3 (2011), pp. 46-50. (胡悦和朱毓朝：《"问题与主义"导向之争: 西方比较政治学沿革及其借鉴意义》，载《天津社会科学》，2011年第3期，第46-50页。)

Tongshun Cheng and Yue Hu. “The Cultural Props of Foreign Policy”. *Tribune of Study* (2010), pp. 33--37.
(程同顺和胡悦：《对外政策的文化道具：浅析文明冲突论的工具性》，载《学习论坛》2010年第26期，第33-37页。)

Yue Hu. “An Analysis of Politics Fixed Position of CPPCC from the Political Scientific Angle”. *Journal of Tianjin Institute of Socialism* (2009), pp. 19--23.
(《从政治科学角度分析人民政协的政治定位》，载《天津市社会主义学院学报》 2009年第1期，第19-23页。)

## Software
```{r echo = FALSE, results = "asis"}
bib[group = "software"]
```

## Under Review

```{r echo = FALSE, results = "asis"}
bib[group = "underreview"]
```

## Working Projects

"Measure Political Desirability: An Experimental Method" (with Wenfang Tang).

"The Logic of Peaceful Rise: Revisiting the Power-Peace Relationship in International Politics" (with Ray Ou-Yang)

"The Popularity of Political Propaganda in Modern China: A Model of Demands" (with Zijie Shao).

"Niche Audience: Chinese Government’s Secret Weapon in Official Media Propaganda" (with Zijie Shao).

# Conferences
* 2017
    + "Cultural Accent vs. Authority Accent: How Does Language Attitude Affect Political Trust."
        + \footnotesize Association of Chinese Political Science (ACPS) Annual Meeting, Tianjin, China, Jun., 9--11.
        + \footnotesize Chinese Political Science and Methods Workshop, Shanghai, China, Jul., 8--9.
        + \footnotesize Political Culture, Psychology, and Behavior Research Workshop, Nanjing, China, Jul., 9--11.
    + "The Weight of History: Explaining the Anti-Japanese Sentiments in the Chinese Circle" (with Amy Liu).
        + \footnotesize Midwest Political Science Association (MPSA) Annual Convention,  Chicago, Illinois, Apr. 7--9.
    + "The Popularity of Political Propaganda in Modern China: A Model of Demands" (with Zijie Shao).
        + \footnotesize Midwest Political Science Association (MPSA) Annual Convention,  Chicago, Illinois, Apr. 7--9.
    + "The Logic of Peaceful Rise" (with Ray Ou-Yang).
        + \footnotesize Midwest Political Science Association (MPSA) Annual Convention,  Chicago, Illinois, Apr. 7--9.
        + \footnotesize International Studies Association (ISA) Annual Convention,  Baltimore, Maryland, Feb. 22--25.
        
* 2016
    + "Measure Political Desirability: A List Experimental Method" (with Wenfang Tang);
    + "Propaganda with Museums: A Spatial Analysis of Patriotic Educational Demonstration Bases in China".
        + \footnotesize Association of Chinese Political Science (ACPS) Annual Meeting, Monterey, California, Oct, 10--11.
    + "Value Promotion, Justification, or Mobilization? The Dynamic of the Discourse on Democracy in Modern China."
        + \footnotesize Midwest Political Science Association (MPSA) Annual Conference, Chicago, Apr., 7-10.
* 2015
    + "Affirmative Inaction: Education, Social Mobility, and Ethnic Inequality in China" (with Wenfang Tang and Shuai Jin).
    + "Language and Political Trust."
        + \footnotesize Midwest Political Science Association (MPSA) Annual Conference, Chicago, Apr., 16--19.
* 2013
    + "Connecting Nationalism and Political Transition:A Study of Nationalist Influence on Political Transition based on the China Case."
        + \footnotesize University of South Carolina Inaugural Graduate Student Conference, Columbia, South Carolina.
* 2012
    + "Twofold-Affecting Model: A Cultural Pattern of Social Change from a Comparative Study between the China and Russia Cases."
        + \footnotesize American Association for Chinese Studies (AACS) Annual Conference, Atlanta, Georgia, Oct. 12-14.

# Researching Program
* Youth Project of National Social Science Foundation of China: Assessing and Improving the Political Ecology of Grassroots Party Organizations (ID: 17CZZ041). 
    + Principal Investigator and Methodology Director\hfill 2017/06-2020/06.

# Research Experience
## Data Collection
* Online survey experiment in China.\hfill 2017-02
    + \footnotesize Designed an online survey experiments, finished 994 surveys.
    
* Field survey experiment in China.\hfill 2016-12
    + \footnotesize Designed and conducted survey experiments in Chengdu and Meizhou of China on 421 subjects in total.

* Web scrapping Newspaper Documents.\hfill 2016
    + \footnotesize Scrapped the text content of *People's Daily* (1946-2003) from a third party website, ending with 1,371,607 documents.

## Research Assistant
* Corruption and Politics in Russia, Ukraine, and Georgia Project (Univ. of Iowa)\hfill 2015-2016
* Standardized World Income Inequality Database Project (Univ. of Iowa)\hfill 2015-05/06
* Survey in Eastern Asia Project (Univ. of South Carolina)\hfill 2013-05/08 


# Teaching Interests
* Comparative Politics: 
    + Intro to Comparative Politics, Language Policy, Public Opinion, Chinese Politics, Asian Politics, Inequality, Democratization and Regime Transition, Nationalism.
* Political Methodology:
    + Intro to Quantitative Analysis in Social Science, Regression, Maximum Likelihood Estimation, Multilevel Modeling, Spatial Analysis, Network Analysis, Experimental Methods, Structural Equation Modeling, Survey Design and Analysis, Data Visualization.
* Professionalism
    + Research Design, Progamming in R and Stata (tutorship on Python and C++)， Professional writing with Latex and Rmarkdown.

# Teaching Experience

## Instructor, University of Iowa

* Designing Political Research\hfill Fall 2017
* Math Camp for Incoming Graduate Students (with Jielu Yao)\hfill Summer 2017
* Introduction to R Workshop Series\hfill 2015-2017
* Multilevel Modeling with Stata and R\hfill 2016-2017
* Math Camp for Incoming Graduate Students (with Shuai Jin)\hfill Summer 2016

## Teaching Assistant, University of Iowa

* Introduction to Political Behavior\hfill Spring 2015
* Introduction to International Relations\hfill Fall 2014
* Introduction to Comparative Politics\hfill Spring 2014
* Political Campaigning\hfill Fall 2014
* Political Psychology\hfill Fall 2014

## Teaching Assistant, University of South Carolina

* International Relations\hfill Spring 2013
* Comparative Politics\hfill Spring 2013
* Controversial World Politics\hfill Fall 2012
* American National Government\hfill Spring 2012
* Comparative Politics-Developing Countries\hfill Spring 2012
* National Security of United States\hfill Fall 2011

## Teaching Assistant, University of Regina

* Introduction to Political Science\hfill Fall 2010

## Guest Lecture, Nankai University
* Investigating Inequality with Real-Life Data: Research Strategies and Methods\hfill Summer 2017

## Guest Lecture, University of South Carolina
* Comparative Politics-Developing Countries\hfill Spring 2012
* National Security of United States\hfill Fall 2011

# Grants
* Ballard and Seashore Fellowship\hfill 2017
* Post-Comprehensive Research Award\hfill 2016
* T. Anne Cleary International Dissertation Research Fellowship\hfill 2016
* Center of Asian and Pacific Studies Graduate Dissertation Grant\hfill 2016
* Best Conference Paper Award of Department of Political Science\hfill 2016
* Graduate Research Award, University of Regina\hfill 2010 
* Graduate Studies Scholarship, University of Regina\hfill 2009-2011
* City Administration Scholarship, Tianjin Municipal People’s Government\hfill 2008


# Professional Affiliation
* Member of American Political Science Association (& Political Communication Section).
* Member of Midwest Political Science Association.
* Member of Association of Chinese Political Science
* Member of American Association for Chinese Studies.

# Skills
* Analysis & Programming: R, Stata, Python, C++, Mathematica, NetLogo, JAGS, UCINET.
* Application:  \LaTeX, Markdown, Git(GitHub).
* Language: English, Chinese (Mandarin)

# References

\begin{tabular}{ll}
\parbox{5cm}{\textbf{Wenfang Tang (Chair)}\\Professor\\University of Iowa\\(319)335-2546\\\href{mailto:wenfang-tang@uiowa.edu}{wenfang-tang@uiowa.edu}}
 &\parbox{5cm}{\textbf{William M. Reisinger}\\Professor\\University of Iowa\\(319)335-2351\\\href{mailto:william-reisinger@uiowa.edu}{william-reisinger@uiowa.edu}}\\
&\\
\parbox{5cm}{\textbf{Frederick Solt}\\Associate Professor\\University of Iowa\\(319) 335-2340\\\href{mailto:frederick-solt@uiowa.edu}{frederick-solt@uiowa.edu}}
 &\parbox{5cm}{\textbf{Caroline J. Tolbert}\\Professor\\University of Iowa\\(319) 335-2471\\\href{caroline-tolbert@uiowa.edu}{caroline-tolbert@uiowa.edu}}\\
\end{tabular}
