---
name: 胡
surname: 悦
address: "清华大学 政治学系"
www: sammo3182.github.io
email: yuehu@tsinghua.edu.cn
github: sammo3182
twitter: yuehupolisci
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "414141"
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=multiple-bibliographies.lua"] # used for creating bibliographies for multiple section
header-includes:
- \usepackage{ctex}
csl: apa.csl # to show the entire list of the authors
bibliography_published: "My_Publications.bib" # use separate .bib files and assign each of them a unique key: bibliography_*
bibliography_chinese: "My_Chinese.bib"
bibliography_software: "My_Software.bib"
bibliography_conference: "My_Conference.bib"
nocite: '@*' # don't change this if you want to print out all the refs
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE)

# R packages --------------------------------------------------------------
if (!require(pacman)) install.packages("pacman"); library(pacman)

p_load_gh("ropenscilabs/tic", "mitchelloharawild/vitae")
p_load(tinytex, scholar, tidyverse, here, readxl, glue, bibtex, rorcid, lubridate, vitae)


# Get latex ---------------------------------------------------------------

## This needs to be run manually if LaTex is not installed locally.
##tinytex::install_tinytex()

```

```{r orcidData, include=FALSE, echo=F,eval=FALSE}

# orcidID <- "0000-0002-2829-3971"

## Education
# df_edu <- rorcid::orcid_educations(orcidID)[[orcidID]]$`affiliation-group`$summaries%>%
#   data.table::rbindlist(fill=T)

### edu_info<-c("education-summary.department-name","education-summary.role-title","education-summary.start-date.year.value","education-summary.end-date.year.value","education-summary.organization.name","education-summary.organization.address.country")

## Qualifications

# df_qualifications <- rorcid::orcid_qualifications(orcidID)[[orcidID]]$`affiliation-group`$summaries%>%
#   data.table::rbindlist(fill=T)

### qualifications_info<-c("qualification-summary.organization.name","qualification-summary.role-title","qualification-summary.end-date.year.value","qualification-summary.end-date.month.value","qualification-summary.organization.address.country")

## jobs
# ProfessionalPositions <-
#   orcid_employments(orcidID)[[orcidID]]$`affiliation-group`$summaries
# 
# for (i in 1:length(ProfessionalPositions)) {
#   if(length(ProfessionalPositions[[i]])==27)
#       {ProfessionalPositions[[i]]$`employment-summary.end-date.year.value` <- "Present"
#       ProfessionalPositions[[i]]$`employment-summary.end-date.month.value` <- ""}
# }
# 
# df_position<-data.table::rbindlist(ProfessionalPositions,fill = T)

# ## works
# benchmark_orcid <- function(id) {
#   tictoc::tic()
#
#   # Get put-codes
#   put_codes = orcid_works(id)[[1]] %>%
#     bind_rows() %>%
#     pull(`put-code`)
#
#   # Get info of those put codes
#   list_orcid <- orcid_works(id, put_code = put_codes) #%>% bind_rows()
#   cat(id, " - ")
#
#   tictoc::toc()
#   list_orcid
# }
#
# works_raw<-benchmark_orcid(orcidID)[[orcidID]][["works"]]
# df_works <-within(works_raw,{
#   authors<-NA
#   authors <- str_extract(`work.citation.citation-value`,"(?<=author=\\s\\{).*(?=\\}, year)")%>%
#     str_replace_all(c("\\{"="","\\}"=""))
# })

##membership
# df_membership <- orcid_memberships(orcidID)[[orcidID]][["affiliation-group"]][["summaries"]]%>%
#   data.table::rbindlist(fill=T)
# membership_info <- c("membership-summary.organization.name","membership-summary.organization.address.country")

#Grants

# df_grants <- orcid_distinctions(orcidID)[[orcidID]][["affiliation-group"]][["summaries"]]%>%
#   data.table::rbindlist(fill = T)

```

# 教育经历

```{r Education}
tribble(   
  ~Year, ~Degree, ~Institution, ~Country,  
  '2013-2018', "哲学博士（Doctor of Philosophy, 政治科学）","爱荷华大学（University of Iowa, Iowa City）", "美国，爱荷华州",  
  '2011-2013', "文学硕士（Master of Arts，政治科学）","南卡罗莱纳大学（University of South Carolina, Columbia）", "美国，南卡罗莱纳州",   
  '2009-2011', "文学硕士（Master of Arts，政治科学）","里贾纳大学（University of Regina, Regina）", "加拿大，萨斯喀彻温省" , 
  '2005-2009', "法学学士（国际关系）","南开大学", "中国，天津") %>%    
  detailed_entries(     
    when = Year,     
    with = Degree,      
    where = Country,
    what = Institution)

# df_edu %>%
#   detailed_entries(
#     with = glue::glue("{`education-summary.role-title`} ({`education-summary.department-name`}) "),
#     when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
#     what = `education-summary.organization.name`,
#     where = `education-summary.organization.address.country`
#   )
```

## 专业训练

```{r Qualifications}
tribble(      
  ~Year, ~Degree, ~Institution, ~Country,     
  '2016-12', "信息学辅修证书（Certificate of Informatics）","爱荷华大学（University of Iowa, Iowa City）", "美国，爱荷华州",    
  '2014-06', "实验研究方法（Experimental Method）","新加坡国立大学", "新加坡",  ) %>% 
  detailed_entries(          
    when = Year,          
    with = Degree,           
    where = Country,     
    what = Institution) 
```

# 工作经历
```{r ProfessionalPositions}
tribble(         
  ~Year, ~Degree, ~Institution, ~Country,        
  '2019-01至今', "助理教授","清华大学社会科学院政治学系", "中国，北京",       
  '2019-06至今', "副主任","清华大学数据与治理中心", "中国，北京",       
  '2015-05 ~ 2018-05', "统计学顾问（Statistical Consultant）","爱荷华社会科学研究中心（Iowa Social Science Research Center）", "美国，爱荷华州") %>%    
  detailed_entries(               
    when = Year,               
    with = Degree,               
    where = Country,          
    what = Institution) 
```

# 论文发表
## **Peer-Review 论文**

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_published}
:::

\endgroup

## **中文论文**

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_chinese}
:::

\endgroup

## **研发软件**

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_software}
:::

\endgroup

# 会议活动

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_conference}
:::

\endgroup


# 荣誉奖励
```{r grants}
tribble(            
  ~Year, ~Award, ~Institution,            
  '2017', "Ballard and Seashore 奖学金","爱荷华大学",         
  '2016', "T. Anne Cleary 国际博士论文奖学金","爱荷华大学", 
  "2016", " Post-Comprehensive 研究奖" ,"爱荷华大学") %>%       
  detailed_entries(                    
    when = Year,                    
    with = Award,                    
    what = Institution) 
```

# 专业技能

## **分析与编程**
R, STATA, Python, C++, Mathematica, NetLogo, JAGS, UCINET

## **应用**
LaTeX, Markdown, Git


# 学术共同体

* 美国政治科学协会（APSA）成员
* 中西部政治科学协会（MPSA）成员
* 中国政治科学研究协会（ACPS）成员

# 教学经历

```{r teaching}
tribble(
  ~Year, ~Name, ~Institution,
  '秋季学期', "70700173: 治理技术专题：政治数据分析","清华大学",
  '秋季学期', "80700673: 政务大数据应用与分析","清华大学",
  '春季学期', "30700953: 公共政策分析：视角与方法","清华大学",
  '夏季学期', "工作坊：数据可视化","清华大学",
  '夏季学期', "工作坊：和Dr.Hu一起学习R","清华大学",
  '2018 秋季学期', "POLI301: 政治数据分析","爱荷华大学",
) %>% 
  detailed_entries(
    when = Year,
    with = Name, 
    where = Institution
  )
```
