\documentclass[10.5pt,]{article}

\usepackage{multicol} % for multiple columns



\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\else % if luatex or xelatex
\ifxetex
\usepackage{xltxtra,xunicode} %originally, \usepackage{mathspec}. This change is to produce Chinese
\else
\usepackage{fontspec}
\fi
\defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
	\usepackage{microtype}
	\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}


% Make lists without bullets
\renewenvironment{itemize}{
	\begin{list}{}{
			\setlength{\leftmargin}{1.5em}
		}
	}{
	\end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}

\usepackage{ctex}
% Siyuan Font
%\setCJKmainfont[BoldFont = Noto Sans CJK SC]{Noto Serif CJK SC}
%\setCJKsansfont{Noto Sans CJK SC}
%\setCJKfamilyfont{zhsong}{Noto Serif CJK SC}
%\setCJKfamilyfont{zhhei}{Noto Sans CJK SC}
%\setCJKfamilyfont{zhkai}{simkai.ttf}

% less space for the Chinese format
\titlespacing\section{0pt}{1pt plus 4pt minus 2pt}{1pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{5pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}


% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}
\newfontfamily\FA{FontAwesome.otf} % Explicitly provide .otf

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
	\cfoot{\scriptsize  Yue Hu - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
		pdftitle={Yue Hu:  CV (Curriculum Vitae)},
			pdfauthor={Yue Hu},
			colorlinks=true,
	linkcolor=blue,
	citecolor=Blue,
	urlcolor=blue,
	breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% try to fit picture


\begin{document}
	
	
	\centerline{\huge \bf Yue Hu}
	
	
	
	\vspace{2 mm}
	
	\hrule
	
	\vspace{2 mm}
	
	
	\moveleft.5\hoffset\centerline{313 Schaeffer Hall, 20E Washington Street, Iowa City, IA, 52242}
	\moveleft.5\hoffset\centerline{ {\FA\faEnvelope} \hspace{1 mm} \href{mailto:}{\tt \href{mailto:yue-hu-1@uiowa.edu}{\nolinkurl{yue-hu-1@uiowa.edu}}} \hspace{1 mm}  {\FA\faPhone} \hspace{1 mm}  +01-803-250-1686  \hspace{1 mm}  {\FA\faGithub} \hspace{1 mm} \href{http://github.com/sammo3182}{\tt sammo3182} \hspace{1 mm}    {\FA\faGlobe} \hspace{1 mm} \href{http://sammo3182.github.io}{\tt sammo3182.github.io}   }
	
	\vspace{2 mm}
	
	\hrule
	
		
	\section{Education}\label{education}

\subsection{Degree}\label{degree}

\begin{itemize}
\tightlist
\item
  Ph.D.~in Political Science, The University of Iowa,
  U.S.A.\hfill 2018-05 (Expected)

  \begin{itemize}
  \tightlist
  \item
    \footnotesize Dissertation: ``Rebuilding the Tower of Babel:
    Language Policy and Political Trust in China.''

    \begin{itemize}
    \tightlist
    \item
      Committee Chair: Wenfang Tang
    \item
      Committee Members: William M. Reisinger, Frederick Solt, Caroline
      J. Tolbert, and David Cassels Johnson (Education)
    \item
      Abstract: My dissertation uncovers a new path by which
      authoritarian governments can impact public attitudes---language
      policy. Conventionally, the policy is regarded as a social
      institution to set the official language and regularize the
      linguistic system of a country. My research argues and
      demonstrates with various empirical evidence that an authoritarian
      government can use it as a political tool to affect citizens'
      political trust and thoughts profoundly. Especially, it empowers
      the official language that the government representatives can use
      to reinforce their political identities and enhance the public
      trust in them. To test this theory, I conducted a series of
      original field experiments with Chinese high school students in
      different areas and found that using the official language
      significantly improved listeners' trust in the bureaucrats and
      this effect closely related to the speakers' political rather than
      cultural identities. My dissertation also uncovers with a modifier
      analysis of a nationally representative survey that official
      language proficiency can adjust Chinese citizens' trust in
      political institutions and uses a computer-assisted text analysis
      of 1,371,607 political articles showing how the government
      strategically manipulates the formal political language system to
      communicate with citizens and influence their political value
      system. My dissertation concludes that an authoritarian government
      can use language policy to affect various levels of public
      political trust through speaking, listening, and reading. It also
      imply the connections and interactions among political trust in
      political actors, political institutions, and political values.
    \end{itemize}
  \end{itemize}
\item
  M.A.~in Political Science, The University of South Carolina,
  U.S.A.\hfill 2013-03
\item
  M.A.~in Political Science, The University of Regina,
  Canada\hfill 2011-03
\item
  LL.B. in International Politics, Nankai University,
  China\hfill 2009-06
\end{itemize}

\subsection{Additional Training}\label{additional-training}

\begin{itemize}
\tightlist
\item
  Certificate in Informatics, The University of Iowa,
  U.S.A.\hfill 2016-12
\item
  Experimental Methods, National University of Singapore (IPSA),
  Singapore \hfill 2014-06/07
\end{itemize}

\section{Professional Positions}\label{professional-positions}

\begin{itemize}
\tightlist
\item
  Statistical Consultant, Iowa Social Science Research Center,
  University of Iowa. 2015-08/present
\end{itemize}

\section{Research Interests}\label{research-interests}

\begin{itemize}
\tightlist
\item
  \emph{Comparative Politics}: Language policy, political communication,
  public opinion.
\item
  \emph{Political Methodology}: Survey experiment, text analysis,
  network analysis, spatial analysis.
\item
  \emph{International Relations}: Public diplomacy, international
  cultural relations, Chinese foreign policy.
\end{itemize}

\section{Publications}\label{publications}

\subsection{Peer-Reviewed Journal
Articles}\label{peer-reviewed-journal-articles}

Frederick Solt, Yue Hu, Kevan Hudson, Jungmin Song, et al. ``Economic
Inequality and Class Consciousness''. \emph{The Journal of Politics}
79.3 (2017), pp.~1079--1083.

Frederick Solt, Yue Hu, Kevan Hudson, Jungmin Song, et al. ``Economic
Inequality and Belief in Meritocracy in the United States''.
\emph{Research and Politics} 3.4 (2016), pp.~1-7.

Wenfang Tang, Yue Hu and Shuai Jin. ``Affirmative Inaction: Language
Education and Labor Mobility among China's Muslim Minorities''.
\emph{Chinese Sociological Review} 4.48 (2016), pp.~346-366.

Yue Hu. ``Institutional Difference and Cultural Difference: A
Comparative Study of Canadian and Chinese Cultural Diplomacy''.
\emph{Journal of American-East Asian Relations} 20.2-3 (2013),
pp.~256-268.

\subsection{Journal Articles in
Chinese}\label{journal-articles-in-chinese}

Yue Hu and Yuchao Zhu. ``\,`Issue-Oriented' vs. `Ism-Oriented':
Indigenizing Political Science in China?''. \emph{Tianjin Social
Science} 3 (2011), pp.~46-50. (胡悦和朱毓朝：《``问题与主义''导向之争:
西方比较政治学沿革及其借鉴意义》，载《天津社会科学》，2011年第3期，第46-50页。)

Tongshun Cheng and Yue Hu. ``The Cultural Props of Foreign Policy''.
\emph{Tribune of Study} (2010), pp.~33--37.
(程同顺和胡悦：《对外政策的文化道具：浅析文明冲突论的工具性》，载《学习论坛》2010年第26期，第33-37页。)

Yue Hu. ``An Analysis of Politics Fixed Position of CPPCC from the
Political Scientific Angle''. \emph{Journal of Tianjin Institute of
Socialism} (2009), pp.~19--23.
(《从政治科学角度分析人民政协的政治定位》，载《天津市社会主义学院学报》
2009年第1期，第19-23页。)

\subsection{Software}\label{software}

Frederick Solt and Yue Hu. ``pewdata: Reproducible Retrieval of Pew
Research Center Datasets''. Available at The Comprehensive R Archive
Network (CRAN). 2016. \url{http://CRAN.R-project.org/package=pewdata}.

Frederick Solt and Yue Hu. ``dotwhisker: Dot-and-Whisker Plots of
Regression Results''. Available at The Comprehensive R Archive Network
(CRAN). 2015. \url{http://CRAN.R-project.org/package=dotwhisker}.

Frederick Solt and Yue Hu. ``interplot: Plot the Effects of Variables in
Interaction Terms''. Available at The Comprehensive R Archive Network
(CRAN). 2015. \url{http://CRAN.R-project.org/package=interplot}.

\subsection{Under Review}\label{under-review}

Vicki Claypool, William Reisinger, Marina Zaloznaya and Yue Hu. ``The
Pernicious Effect of Petty Corruption on System-Supporting Political
Behavior in Post-Soviet States''.

Yue Hu. ``Are Informal Education Facilities Effective Means for
Political Propaganda? A Spatial Analysis''.

Yue Hu. ``Strategic Communication: Why the Chinese Government Engages in
Discourse about Democracy and Why It Matters''.

Amy Liu and Yue Hu. ``The Effects of Foreign Language Proficiency on
Public Attitudes: Evidence from the Chinese-Speaking World''.

\subsection{Working Projects}\label{working-projects}

``Measure Political Desirability: An Experimental Method'' (with Wenfang
Tang).

``The Logic of Peaceful Rise: Revisiting the Power-Peace Relationship in
International Politics'' (with Ray Ou-Yang)

``The Popularity of Political Propaganda in Modern China: A Model of
Demands'' (with Zijie Shao).

``Niche Audience: Chinese Government's Secret Weapon in Official Media
Propaganda'' (with Zijie Shao).

\section{Conferences}\label{conferences}

\begin{itemize}
\tightlist
\item
  2017

  \begin{itemize}
  \tightlist
  \item
    ``Cultural Accent vs.~Authority Accent: How Does Language Attitude
    Affect Political Trust.''

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Association of Chinese Political Science (ACPS)
      Annual Meeting, Tianjin, China, Jun., 9--11.
    \item
      \footnotesize Chinese Political Science and Methods Workshop,
      Shanghai, China, Jul., 8--9.
    \item
      \footnotesize Political Culture, Psychology, and Behavior Research
      Workshop, Nanjing, China, Jul., 9--11.
    \end{itemize}
  \item
    ``The Weight of History: Explaining the Anti-Japanese Sentiments in
    the Chinese Circle'' (with Amy Liu).

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Midwest Political Science Association (MPSA) Annual
      Convention, Chicago, Illinois, Apr. 7--9.
    \end{itemize}
  \item
    ``The Popularity of Political Propaganda in Modern China: A Model of
    Demands'' (with Zijie Shao).

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Midwest Political Science Association (MPSA) Annual
      Convention, Chicago, Illinois, Apr. 7--9.
    \end{itemize}
  \item
    ``The Logic of Peaceful Rise'' (with Ray Ou-Yang).

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Midwest Political Science Association (MPSA) Annual
      Convention, Chicago, Illinois, Apr. 7--9.
    \item
      \footnotesize International Studies Association (ISA) Annual
      Convention, Baltimore, Maryland, Feb. 22--25.
    \end{itemize}
  \end{itemize}
\item
  2016

  \begin{itemize}
  \tightlist
  \item
    ``Measure Political Desirability: A List Experimental Method'' (with
    Wenfang Tang);
  \item
    ``Propaganda with Museums: A Spatial Analysis of Patriotic
    Educational Demonstration Bases in China''.

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Association of Chinese Political Science (ACPS)
      Annual Meeting, Monterey, California, Oct, 10--11.
    \end{itemize}
  \item
    ``Value Promotion, Justification, or Mobilization? The Dynamic of
    the Discourse on Democracy in Modern China.''

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Midwest Political Science Association (MPSA) Annual
      Conference, Chicago, Apr., 7-10.
    \end{itemize}
  \end{itemize}
\item
  2015

  \begin{itemize}
  \tightlist
  \item
    ``Affirmative Inaction: Education, Social Mobility, and Ethnic
    Inequality in China'' (with Wenfang Tang and Shuai Jin).
  \item
    ``Language and Political Trust.''

    \begin{itemize}
    \tightlist
    \item
      \footnotesize Midwest Political Science Association (MPSA) Annual
      Conference, Chicago, Apr., 16--19.
    \end{itemize}
  \end{itemize}
\item
  2013

  \begin{itemize}
  \tightlist
  \item
    ``Connecting Nationalism and Political Transition:A Study of
    Nationalist Influence on Political Transition based on the China
    Case.''

    \begin{itemize}
    \tightlist
    \item
      \footnotesize University of South Carolina Inaugural Graduate
      Student Conference, Columbia, South Carolina.
    \end{itemize}
  \end{itemize}
\item
  2012

  \begin{itemize}
  \tightlist
  \item
    ``Twofold-Affecting Model: A Cultural Pattern of Social Change from
    a Comparative Study between the China and Russia Cases.''

    \begin{itemize}
    \tightlist
    \item
      \footnotesize American Association for Chinese Studies (AACS)
      Annual Conference, Atlanta, Georgia, Oct. 12-14.
    \end{itemize}
  \end{itemize}
\end{itemize}

\section{Researching Program}\label{researching-program}

\begin{itemize}
\tightlist
\item
  Youth Project of National Social Science Foundation of China:
  Assessing and Improving the Political Ecology of Grassroots Party
  Organizations (ID: 17CZZ041).

  \begin{itemize}
  \tightlist
  \item
    Principal Investigator and Methodology
    Director\hfill 2017/06-2020/06.
  \end{itemize}
\end{itemize}

\section{Research Experience}\label{research-experience}

\subsection{Data Collection}\label{data-collection}

\begin{itemize}
\tightlist
\item
  Online survey experiment in China.\hfill 2017-02

  \begin{itemize}
  \tightlist
  \item
    \footnotesize Designed an online survey experiments, finished 994
    surveys.
  \end{itemize}
\item
  Field survey experiment in China.\hfill 2016-12

  \begin{itemize}
  \tightlist
  \item
    \footnotesize Designed and conducted survey experiments in Chengdu
    and Meizhou of China on 421 subjects in total.
  \end{itemize}
\item
  Web scrapping Newspaper Documents.\hfill 2016

  \begin{itemize}
  \tightlist
  \item
    \footnotesize Scrapped the text content of \emph{People's Daily}
    (1946-2003) from a third party website, ending with 1,371,607
    documents.
  \end{itemize}
\end{itemize}

\subsection{Research Assistant}\label{research-assistant}

\begin{itemize}
\tightlist
\item
  Corruption and Politics in Russia, Ukraine, and Georgia Project (Univ.
  of Iowa)\hfill 2015-2016
\item
  Standardized World Income Inequality Database Project (Univ. of
  Iowa)\hfill 2015-05/06
\item
  Survey in Eastern Asia Project (Univ. of South
  Carolina)\hfill 2013-05/08
\end{itemize}

\section{Teaching Interests}\label{teaching-interests}

\begin{itemize}
\tightlist
\item
  Comparative Politics:

  \begin{itemize}
  \tightlist
  \item
    Intro to Comparative Politics, Language Policy, Public Opinion,
    Asian Politics, Chinese Politics, Ethnicity, Nationalism,
    Democratization.
  \end{itemize}
\item
  Political Methodology:

  \begin{itemize}
  \tightlist
  \item
    Research Design, Intro to Quantitative Analysis in Social Science,
    Regression, Maximum Likelihood Estimation, Multilevel Modeling,
    Spatial Analysis, Network Analysis, Experiment, Structural Equation
    Modeling, Survey Design and Analysis, Programming in R, Stata, and
    Python, Data Visualization.
  \end{itemize}
\end{itemize}

\section{Teaching Experience}\label{teaching-experience}

\subsection{Instructor, University of
Iowa}\label{instructor-university-of-iowa}

\begin{itemize}
\tightlist
\item
  Designing Political Research\hfill Fall 2017
\item
  Math Camp for Incoming Graduate Students (with Jielu Yao)\hfill Summer
  2017
\item
  Introduction to R Workshop Series\hfill 2015-2017
\item
  Multilevel Modeling with Stata and R\hfill 2016-2017
\item
  Math Camp for Incoming Graduate Students (with Shuai Jin)\hfill Summer
  2016
\end{itemize}

\subsection{Teaching Assistant, University of
Iowa}\label{teaching-assistant-university-of-iowa}

\begin{itemize}
\tightlist
\item
  Introduction to Political Behavior\hfill Spring 2015
\item
  Introduction to International Relations\hfill Fall 2014
\item
  Introduction to Comparative Politics\hfill Spring 2014
\item
  Political Campaigning\hfill Fall 2014
\item
  Political Psychology\hfill Fall 2014
\end{itemize}

\subsection{Teaching Assistant, University of South
Carolina}\label{teaching-assistant-university-of-south-carolina}

\begin{itemize}
\tightlist
\item
  International Relations\hfill Spring 2013
\item
  Comparative Politics\hfill Spring 2013
\item
  Controversial World Politics\hfill Fall 2012
\item
  American National Government\hfill Spring 2012
\item
  Comparative Politics-Developing Countries\hfill Spring 2012
\item
  National Security of United States\hfill Fall 2011
\end{itemize}

\subsection{Teaching Assistant, University of
Regina}\label{teaching-assistant-university-of-regina}

\begin{itemize}
\tightlist
\item
  Introduction to Political Science\hfill Fall 2010
\end{itemize}

\subsection{Guest Lecture, Nankai
University}\label{guest-lecture-nankai-university}

\begin{itemize}
\tightlist
\item
  Investigating Inequality with Real-Life Data: Research Strategies and
  Methods\hfill Summer 2017
\end{itemize}

\subsection{Guest Lecture, University of South
Carolina}\label{guest-lecture-university-of-south-carolina}

\begin{itemize}
\tightlist
\item
  Comparative Politics-Developing Countries\hfill Spring 2012
\item
  National Security of United States\hfill Fall 2011
\end{itemize}

\section{Grants}\label{grants}

\begin{itemize}
\tightlist
\item
  Post-Comprehensive Research Award\hfill 2016
\item
  T. Anne Cleary International Dissertation Research
  Fellowship\hfill 2016
\item
  Center of Asian and Pacific Studies Graduate Dissertation
  Grant\hfill 2016
\item
  Best Conference Paper Award of Department of Political
  Science\hfill 2016
\item
  Graduate Research Award, University of Regina\hfill 2010
\item
  Graduate Studies Scholarship, University of Regina\hfill 2009-2011
\item
  City Administration Scholarship, Tianjin Municipal People's
  Government\hfill 2008
\end{itemize}

\section{Professional Affiliation}\label{professional-affiliation}

\begin{itemize}
\tightlist
\item
  Member of American Political Science Association (\& Political
  Communication Section).
\item
  Member of Midwest Political Science Association.
\item
  Member of Association of Chinese Political Science
\item
  Member of American Association for Chinese Studies.
\end{itemize}

\section{Skills}\label{skills}

\begin{itemize}
\tightlist
\item
  Analysis \& Programming: R, Stata, Python, C++, Mathematica, NetLogo,
  JAGS, UCINET.
\item
  Application: \LaTeX, Markdown, Git(GitHub).
\item
  Language: English, Chinese (Mandarin)
\end{itemize}

\section{References}\label{references}

\begin{tabular}{ll}
\parbox{5cm}{\textbf{Wenfang Tang (Chair)}\\Professor\\University of Iowa\\(319)335-2546\\\href{mailto:wenfang-tang@uiowa.edu}{wenfang-tang@uiowa.edu}}
 &\parbox{5cm}{\textbf{William M. Reisinger}\\Professor\\University of Iowa\\(319)335-2351\\\href{mailto:william-reisinger@uiowa.edu}{william-reisinger@uiowa.edu}}\\
&\\
\parbox{5cm}{\textbf{Frederick Solt}\\Associate Professor\\University of Iowa\\(319) 335-2340\\\href{mailto:frederick-solt@uiowa.edu}{frederick-solt@uiowa.edu}}
 &\parbox{5cm}{\textbf{Caroline J. Tolbert}\\Professor\\University of Iowa\\(319) 335-2471\\\href{caroline-tolbert@uiowa.edu}{caroline-tolbert@uiowa.edu}}\\
\end{tabular}
	
			\end{document}