---
output: 
  ## rticles::ctex: Chinese
  pdf_document:
    keep_tex: yes
    latex_engine: pdflatex
    template: svm-latex-cv.tex
geometry: margin=1in

title: "CV"
author: Yue Hu

jobtitle: "PhD Candidate, Statistical Consultant (ISRC)"
address: "313 Schaeffer Hall, 20E Washington Street, Iowa City, IA, 52242"
fontawesome: yes
email: yue-hu-1@uiowa.edu
github: sammo3182
phone: "+01-803-250-1686"
web: sammo3182.github.io
updated: no
fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 10.5pt
linkcolor: blue
urlcolor: blue
---

```{r setup, include=FALSE}
library(RefManageR)
# custom <- RefManageR:::MakeBibLaTeX()
# custom$fmtJournal <- function(s){
#                                 if (length(s$journaltitle)) {
#                                     res <- emph(cleanupLatex(s$journaltitle))
#                                     if (length(s$journalsubtitle))
#                                         res <- paste(addPeriod(res), emph(cleanupLatex(s$journalsubtitle)))
#                                     return(res)
#                                 }
#                                 else if (!is.null(s$journal)) {
#                                     emph(cleanupLatex(s$journal))
#                                 }
#                             }

bib <- ReadBib("publication.bib", check = "error")
BibOptions(check.entries = FALSE, 
           first.inits = FALSE,
           bib.style = "authoryear",
           # style = "latex",
           max.names = 2,
           dashed = FALSE,
           sorting = "ydnt")
```

# Education
## Degree
Ph.D. in Political Science, The University of Iowa, U.S.A.\hfill 2017-05(Expected)

> \footnotesize Dissertation: "Dominant Language: A Political Stabilizer"

Certificate in Informatics, The University of Iowa, U.S.A.\hfill 2017-01

M.A. in Political Science, The University of South Carolina, U.S.A.\hfill 2013-03

> \footnotesize Thesis: "Connecting Nationalism and Political Transition: A Study of Nationalist Influence on Political Transition Based on the Chinese Case."

LL.B. in International Politics, Nankai University, China\hfill 2009-06

# Professional Training
Experimental Methods \hfill 2014-06/07

> \footnotesize IPSA-NUS Summer School of Social Science Research Methods, Singapore.

# Professional Positions
Statistical Consultant, Iowa Social Science Research Center, University of Iowa.

# Publication
## Journal Articles
```{r echo = FALSE, results = "asis"}
bib[group = "published"]
```

## Software
```{r echo = FALSE, results = "asis"}
bib[group = "software"]
```

## Under Review
Claypool, Vicki William Reisinger, Marina Zaloznaya, and Yue Hu, "The Pernicious Effect of Petty Corruption on System-Supporting Political Behavior in Post-Soviet States."

Hu, Yue, "Strategic Communication: Why the Chinese Government Engages in Discourse about Democracy and Why It Matters."

Hu, Yue, "Are Informal Education Facilities Effective Means for Political Propaganda? A Spatial Analysis."

## Working Projoects

"Measure Political Desirability: An Experimental Method" (with Wenfang Tang).

"The Weight of History: Explaining the Anti-Japanese Sentiments in the Chinese Circle" (with Amy Liu).

"The Popularity of Political Propaganda in Modern China: A Model of Demands" (with Zijie Yao).

"Niche Audience: Chinese Government’s Secret Weapon in Official Media Propaganda" (with Zijie Shao).

"The Logic of Peaceful Rise: Revisiting the Power-Peace Relationship in International Politics" (with Ray Ou-Yang)


## Magazine and Others
```{r echo = FALSE, results = "asis"}
bib[group = "others"]
```


# Conference
## 2017
"The Logic of Peaceful Rise" (with Ray Ou-Yang).

> \footnotesize International Studies Association Annual Convention,  Baltimore, Maryland, Feb. 22~25.

## 2016
"Measure Political Desirability: A List Experimental Method" (with Wenfang Tang);

"Propaganda with Museums: A Spatial Analysis of Patriotic Educational Demonstration Bases in China".

> \footnotesize Association of Chinese Political Science Annual Meeting, Monterey, California, Oct, 10-11.

"Value Promotion, Justification, or Mobilization? The Dynamic of the Discourse on Democracy in Modern China."

> \footnotesize Midwest Political Science Association Annual Conference, Chicago, Apr., 7-10.

## 2015
"Affirmative Inaction: Education, Social Mobility, and Ethnic Inequality in China" (with Shuai Jin and Wenfang Tang).
"Language and Political Trust."

> \footnotesize Midwest Political Science Association Annual Conference, Chicago, Apr., 16-19.

## 2013
"Connecting Nationalism and Political Transition:A Study of Nationalist Influence on Political Transition based on the China Case."

> \footnotesize University of South Carolina Inaugural Graduate Student Conference, Columbia, South Carolina.

## 2012
"Twofold-Affecting Model: A Cultural Pattern of Social Change from a Comparative Study between the China and Russia cases."

> \footnotesize American Association for Chinese Studies Annual Conference, Atlanta, Georgia, Oct. 12-14.

## 2011
"Culture and Cultural Diplomacy of Canada and China: A Comparative Study."

> \footnotesize Workshop of Canada-China Relations: Past, Present and Future,
Regina, Saskatchewan, Oct. 7-8.

## 2010
"The Development of Western Comparative Politics and Indigenizing Political Science in China."

> \footnotesize International Conference on "Chinese Political Research: Theories & Methods," Tianjin, Sep 25-26.

## 2008
"The Study of Shanghai Cooperation Organization: The Way for China to Strive for A Position of Local Dominant Power."

> \footnotesize National East Asia Forum for College Students, Beijing, Mar. 28-30.