%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,10pt]{article} % Default font size and paper size


\usepackage{fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin} % Main document font
\setmainfont[Path=./,Extension=.otf,
UprightFont=*-Regular,
ItalicFont=*-Italic,
BoldFont=*-Bold,
SmallCapsFont=*-SmallCaps]{Fontin}

\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

%\usepackage{fullpage}
\usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be \usepackage{fullpage}
% To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}
\addtolength{\textwidth}{2cm}
\addtolength{\hoffset}{-1cm}

\addtolength{\textheight}{2cm}
\addtolength{\voffset}{-1cm}

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{12pt plus 4pt minus 2pt}{3pt} % Spacing around sections
%\titlespacing{command}{left spacing}{before spacing}{after spacing}[right]
%           12pt is what we would like the spacing to be
%           plus 4pt means that TeX can stretch it by at most 4pt
%           minus 2pt means that TeX can shrink it by at most 2pt

\usepackage{longtable}

% Make lists without bullets
\renewenvironment{itemize}{
	\begin{list}{}{
			\setlength{\leftmargin}{1.5em}
		}
	}{
\end{list}
}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

\def\name{\textbf{HU, Yue}}
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}


\begin{document}

%\pagestyle{empty} % Removes page numbering

\font\fb=''[cmr10]'' % Change the font of the \LaTeX command under the skills section


\par{\centering{\Huge \textsc{Hu}, Yue}\bigskip\par} % Your name

\section{Education}
	\subsection*{Degree}
		\begin{tabular}{rp{0.8\textwidth}}	
			\textsc{Present} 2016 & Ph.D. Candidate ABD in Political Science, \textbf{The University of Iowa}, U.S.A.\\
			& \footnotesize Dissertation: ``Dominant Language: A Political Stabilizer'' \\
			& Certificate in Informatics, \textbf{The University of Iowa}.\\[5pt]
			
			\textsc{May} 2013& M.A. in Political Science, \textbf{The University of South Carolina}, U.S.A.\\
			& \footnotesize Thesis: ``Connecting Nationalism and Political Transition: A Study of Nationalist Influence on Political Transition Based on the Chinese Case.'' \\[5pt]
			
			\textsc{March} 2011& M.A. in Political Science, \textbf{The University of Regina}, Canada\\
			& \footnotesize Thesis: ``Culture and Cultural Diplomacy: A Comparative Study of a Canadian and Chinese Case.'' \\[5pt]
			
			\textsc{June} 2009& LL.B. in International Politics, \textbf{Nankai University}, China
		\end{tabular}
	
	\subsection*{Professional Training}
		\begin{tabular}{rp{0.75\textwidth}}	
			\textsc{30 June-11 July}& Experimental Methods,\\
			2014& The 3rd Annual IPSA-NUS Summer School of Social Science Research Methods, Singapore. 
		\end{tabular}



\section{Professional Positions}
		 Statistical Consultant, Iowa Social Science Research Center, University of Iowa.




\section{Research Interests}
	\begin{tabular}{rp{0.65\textwidth}}
		\textsc{Comparative Politics} & Public opinion, political trust, political transformation, nationalism, political culture, China study. \\[5pt]
		\textsc{Methodology} & Survey experiment, text analysis, network analysis, spatial analysis. \\[5pt]
		\textsc{International Relations} & Unconventional security, cultural diplomacy, international cultural relations, Chinese foreign policy. 
	\end{tabular}


\section{Publication}
	\subsection*{Journal Articles}
		\begin{itemize}
			\item Solt, Frederick, \textbf{Yue Hu}, Kevan Hudson, Jungmin Song, and Dong `Erico' Yu. ``Economic Inequality and Belief in Meritocracy in the United States.'' \textit{Research and Politics}, 3-4 (2016): DOI: 10.1177/2053168016672101.
			\item Tang, Wenfang, \textbf{Yue Hu}, and Shuai Jin. ``Affirmative Inaction: Education, Social Mobility, and Ethnic Inequality in China.'' \textit{Chinese Sociological Review}, 48-4 (2016): 346-66.
			\item \textbf{Hu, Yue}. ``Institutional Difference and Cultural Difference: A Comparative Study of Canadian and Chinese Cultural Diplomacy.'' \textit{Journal of American-East Asian Relations} 20.2-3 (2013): 256-68.
			%\item \textbf{Hu, Yue}. ``Canadian and Chinese Cultural Diplomatic Institutions: In a Comparative View.'' [In Chinese]. \textit{Canadian Study} vol. 1 (2013): 181-93.
			\item \textbf{Hu, Yue} and Yuchao Zhu. ```Issue-Oriented' vs. `Ism-Oriented': Indigenizing Political Science in China?'' [In Chinese]. \textit{Tianjin Social Science} vol.3 (2011): 46-50.
			\item Cheng, Tongshun and \textbf{Yue Hu}. ``The Cultural Props of Foreign Policy.'' [In Chinese]. \textit{Tribune of Study} vol.26 (2010): 33-7.
			\item \textbf{Hu, Yue}. ``An Analysis of Politics Fixes Position of CPPCC from the Political Scientific Angle.'' [In Chinese]. Journal of Tianjin Institute of Socialism vol.1 (2009): 19-23.
		\end{itemize}
	
	\subsection*{Software}
		\begin{itemize}
			\item Solt, Frederick and \textbf{Yue Hu}. ``interplot: Plot the Effects of Variables in Interaction Terms.'' CRAN, \url{http://CRAN.R-project.org/package=interplot}.
			\item Solt, Frederick and \textbf{Yue Hu}. ``dotwhisker: Dot-and-Whisker Plots of Regression Coefficients from Tidy Data Frames.'' CRAN, \url{http://CRAN.R-project.org/package=dotwhisker}.
			\item Solt, Frederick and \textbf{Yue Hu}. ``pewdata: Reproducible Retrieval of Pew Research Center Datasets.'' CRAN, \url{http://CRAN.R-project.org/package=pewdata}.
		\end{itemize}
	
	\subsection*{Under Review}
		\begin{itemize}
			\item Solt, Frederick, \textbf{Yue Hu}, Kevan Hudson, Jungmin Song, and Dong `Erico' Yu. ``Economic Inequality and Class Consciousness.'' 
			\item \textbf{Hu, Yue}. ``Strategic Communication: Why the Chinese Government Engages in Discourse about Democracy and Why It Matters'' 
		\end{itemize}
		
	\subsection*{Working Project}
		\begin{itemize}
			\item ``Propaganda with Museums? A Spatial Analysis in China.''
			\item ``Measure Political Desirability: An Experimental Method'' (with Wenfang Tang).
			\item ``The Pernicious Effect of Petty Corruption on System-Supporting Political Behavior in Post-Soviet States'' (with Claypool, Vicki,  William Reisinger, and Marina Zaloznaya).
			\item ``Emerging Empirical Methods of Political Communication Researches in the World.'' [In Chinese].
		\end{itemize}
		
	\subsection*{Other Publications}
	\begin{itemize} 
		\item \textbf{Hu, Yue}. ``Experiences on Document Preparation for Applications to PhD Programs of American Universities.'' [In Chinese]. \textit{New Vision} vol.17 (2014): 37-8.
		\item \textbf{Hu, Yue}. ``Nothing Honored, So...'' [In Chinese]. \textit{New Vision} vol.3 (2010): 25-6.
		\item \textbf{Hu, Yue}. ``Three Harmonies of Premier Zhou Enlai.'' [In Chinese]. \textit{National Spirit} vol. 17 (2007):45.
		\item \textbf{Hu, Yue}. ``Philo-mathematics: A Methodology of Politicians.'' [In Chinese]. \textit{Beauty of Mathematics} vol. 1 (2006):157-60.
		\item \textbf{Hu, Yue}. ``The Greatness of Open Sources.'' [In Chinese]. \textit{LUPA-STAR Essay Compilation} (2006):24-5.
	\end{itemize}


\section{Conference}
	\begin{longtable}{r|p{0.8\textwidth}}
		2016& ``Propaganda with Museums: A Spatial Analysis of Patriotic Educational Demonstration Bases in China.'' Paper presented at \textbf{ACPS}, Monterey, California, October 10-11.\\
		& ``Measure Political Desirability: A List Experimental Method.'' Paper presented with Wenfang Tang at \textbf{ACPS}, Monterey, California, October 10-11.\\
		& ``Value Promotion, Justification, or Mobilization? The Dynamic of the Discourse on Democracy in Modern China.'' Paper presented at \textbf{MPSA}, Chicago, April, 7-10. \\
		\multicolumn{2}{c}{} \\
			
		2015& ``Language and Political Trust.'' Paper presented at \textbf{MPSA}, Chicago, April, 16-19.\\
			& ``Affirmative Inaction: Education, Social Mobility, and Ethnic Inequality in China.'' Paper presented with Shuai Jin at \textbf{MPSA}, Chicago, April, 16-19. \\
		\multicolumn{2}{c}{} \\
		
		2013& ``Connecting Nationalism and Political Transition:A Study of Nationalist Influence on Political Transition based on the China Case.'' Paper presented at \textbf{University of South Carolina Inaugural Graduate Student Conference}, Columbia, South Carolina\\
		\multicolumn{2}{c}{} \\
		
		2012& ``Twofold-Affecting Model: A Cultural Pattern of Social Change from a Comparative Study between the China and Russia cases.'' Paper presented at the \textbf{American Association for Chinese Studies} $54^th$ Annual Conference, Georgia Tech, Atlanta, October 12-14.\\
		\multicolumn{2}{c}{} \\
		
		2011& ``Culture and Cultural Diplomacy of Canada and China: A Comparative Study.'' Paper presented at the Workshop on \textbf{``Canada-China Relations: Past, Present and Future,''} Regina, Saskatchewan, October 7-8.\\
			& ``Two-fold Affecting Model: A Pattern of Cultural Influence on the Development of China.'' Paper presented at the $6^th$ \textbf{Annual University of Regina Graduate and Undergraduate Research Conference}, Regina, Saskatchewan, April 1-2.\\
		\multicolumn{2}{c}{} \\
			
		2010& ``The Development of Western Comparative Politics and Indigenizing Political Science in China.'' Paper presented at the International Conference on ``\textbf{Chinese Political Research: Theories \& Methods},'' Tianjin, September 25-26.\\
			& ``Is the Global Multicultural Structure Tendency Inevitable?'' Paper presented at the $5^th$ \textbf{Annual University of Regina Graduate and Undergraduate Research Conference}, Regina, Saskatchewan, March 12-13.\\
		\multicolumn{2}{c}{} \\
		
		2008& ``The Study of Shanghai Cooperation Organization: The Way for China to Strive for A Position of Local Dominant Power.'' Paper presented at the $3^rd$ \textbf{National East Asia Forum of Undergraduate Students}, Beijing, March 28-30.
	\end{longtable}



\section{Employment}
	\subsection*{Research Related}
		\begin{tabular}{r|p{0.8\textwidth}}
			\textsc{Present}&  Statistical Consultant,\\
			2015& \small Iowa Social Science Research Center, University of Iowa. \\
			\multicolumn{2}{c}{} \\
			
			\textsc{2016}& Research Assistant, empirical analysis and paper writing,\\
			2015& \small with Professors Vicki Claypool, William Reisinger, Marina Zaloznaya, Dept. of Political Science \& Dept. of Sociology, University of Iowa. \\
			\multicolumn{2}{c}{} \\
			
			\textsc{May-June}& Research Assistant, data collection and management for SWIID updates,\\
			2015& \small with Professor Frederick Solt, Dept. of Political Science, University of Iowa. \\
			\multicolumn{2}{c}{} \\
			
			\textsc{May-August}& Research Assistant, survey data collection for East Asian countries,\\
			2013& \small with Professor John Fuh-sheng Hsieh. Dept. of Political Science, University of South Carolina.
		\end{tabular}
	
	\subsection*{Teaching Related}
		\begin{longtable}{r|p{0.8\textwidth}}	
			\textsc{2016}& Instructor,\\
			2015& \small Course:\textbf{ Hello, R: A Introduction To R}, Iowa Social Science Research Center, University of Iowa.\\
			\multicolumn{2}{c}{} \\
			
			\textsc{Jan.-May}& Teaching Assistant, instructor of discussion sections,\\
			2015& \small Course: \textbf{Introduction to Political Behavior} (030:050), University of Iowa.\\
			\multicolumn{2}{c}{} \\
			
			\textsc{Sep.-Dec.}& Teaching Assistant, instructor of discussion sections, \\
			2014& \small Course: \textbf{Introduction to International Relations} (030:060), University of Iowa.\\
			\multicolumn{2}{c}{} \\
			
			\textsc{Jan.-May}& Teaching Assistant, instructor of discussion sections, \\
			2014& \small Course: \textbf{Introduction to Comparative Politics} (030:045), University of Iowa.\\
			\multicolumn{2}{c}{} \\
			
			\textsc{Sep.-Dec.}& Teaching Assistant, designing exams and leading lectures. \\
			2013& \small Course: \textbf{Political Campaigning }(030:127); \textbf{Political Pschology} (030: 154), University of Iowa.\\
			\multicolumn{2}{c}{} \\
			
			\textsc{Jan.-May}& Teaching Assistant, instructor of discussion sections, \\
			2013& \small Course: \textbf{International Relations} (POLI-315); \textbf{Comparative Politics} (POLI-316), University of South Carolina.\\
			\multicolumn{2}{c}{} \\
			
			\textsc{Sep.-Dec.}& Teaching Assistant, designing exams and leading lectures. \\
			2012& \small Course: \textbf{Controversial World Politics} (POLI-101), University of South Carolina.\\
			\multicolumn{2}{c}{} \\
			
			\textsc{Jan.-May}& Teaching Assistant, designing exams and leading lectures. \\
			2012& \small Course: \textbf{American National Government} (POLI-201); \textbf{Comparative Politics-Developing Countries} (POLI-380), University of South Carolina.\\
			\multicolumn{2}{c}{} \\

			\textsc{Sep.-Dec.}& Teaching Assistant, designing exams and leading lectures. \\
			2011& \small Course: \textbf{National Security of United States} (POLI-342), University of South Carolina.\\
			\multicolumn{2}{c}{} \\
			
			\textsc{Sep.-Dec.}& Seminar Leader (GTA), designing and leading undergraduate seminars. \\
			2010& \small Course: \textbf{Introduction to Political Science} (PSCI-100), University of Regina, Canada.			
		\end{longtable}

\section{Honors, Awards, \& Fellowship}
\begin{itemize}
	\item T. Anne Cleary International Dissertation Research Fellowship, Univ. of Iowa, 2016 (amount: \$5,000). 
	\item ``Best Conference Paper Award,'' Department of Political Science, 2016 (\textit{awarded to only one student with high-quality presentations in national academic conferences}).
	\item Graduate Assistantship, University of South Carolina, 2011, 2012, 2013 (\textit{tuition abatement and stipend, awarded to less than one-third of the graduate students on a competitive basis}).
	\item Graduate Studies Scholarship, University of Regina, 2009, 2011 (\textit{awarded to students of high academic standing based on the overall course marks, publications, and the supervisor's evaluation of the student's progress}).
	\item Graduate Research Award, University of Regina, 2010 (\textit{awarded to students of high academic standing on a competitive basis}).
	\item City Administration Scholarship, Tianjin Municipal People's Government, 2008 (\textit{awarded to the top 2\% college students of high academic standing in the university}).
\end{itemize}

\section{Professional Affiliation}
\begin{itemize}
	\item Member of American Political Science Association.
	\item Member of Midwest Political Science Association.
	\item Member of Association of Chinese Political Science
	\item Member of American Association for Chinese Studies.
\end{itemize}


\section{Languages}

\begin{tabular}{rl}
	\textsc{Chinese(Mandarin):} & Native\\
	\textsc{English:} & Fluent
\end{tabular}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS 
%----------------------------------------------------------------------------------------

\section{Skills}
\begin{tabular}{rl}
	Analysis \& Programming: & R, \textsc{Stata}, \textsc{Python}, \textsc{C++}, \textsc{Mathematica}, \textsc{NetLogo}.\\
	Editing: & {\fb \LaTeX}\setmainfont[SmallCapsFont=Fontin SmallCaps]{Fontin-Regular}, Markdown.
\end{tabular}


\section{Contact Informaiton}
\begin{tabular}{rl}
	\textsc{Institution:} &  \href{http://clas.uiowa.edu/polisci/}{Department of Political Science}, University of Iowa.\\
	\textsc{Office:} & 313 Schaeffer Hall, Iowa City, IA 52242-1409.\\
	\textsc{Phone:} & +1 319-335-2370\\
	\textsc{Email:} & \href{mailto:yue-hu-1@uiowa.edu}{yue-hu-1@uiowa.edu}\\
	\textsc{Homepage:} & \href{http://sammo3182.github.io}{http://sammo3182.github.io}
\end{tabular}

% Footer
\begin{center}
	\begin{footnotesize}
		Last updated: \today \\
		\href{\footerlink}{\texttt{\footerlink}}
	\end{footnotesize}
\end{center}

\end{document}
